---
title: "TRhizo-urbanMicrobiome"
subtitle: "Pathogenic Bacteria"
author: "David Murray-Stoker"
output:
  pdf_document:
    toc: true
    toc_depth: 5
    fig_caption: yes
    latex_engine: xelatex
always_allow_html: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(results = "hold", fig.pos = "H", fig.align = "center", out.width = "92.5%")
options(knitr.graphics.error = FALSE)
kableExtra::usepackage_latex("float")
```

```{r Load Packages for R Markdown, include = FALSE}
library(kableExtra)
library(knitr)
```





\newpage
# Load Packages

\vspace{10pt}

```{r Load Packages, include = FALSE}
## Load the tidyverse
library(tidyverse)

## Packages for analyses
library(broom)
library(easystats)
library(mgcv)
library(tidyamplicons)
```





\newpage
# Load Data

\vspace{10pt}

```{r Load Data, echo = TRUE}
## Microbiome tidyamplicons
microbiome.tidyamplicon.reference <- read_rds(
	file = "data/microbiome_tidyamplicon_reference.rds"
)

## Load the urbanization data
urbanization.data <- read_rds(
	file = "data/urbanization_data.rds"
)

## Load the workspace
#load("data_analysis/10-bacterial_functional_groups/pathogenic_bacteria-workspace.RData")
```







\newpage
# Data Management

\vspace{10pt}

```{r Data Management, echo = TRUE}
## Set reference ASV abundance matrix
ASV.abundance.matrix <- add_rel_abundance(microbiome.tidyamplicon.reference) %>%
  abundances()

## Set reference taxa matrix
ASV.taxa.matrix <- taxa(microbiome.tidyamplicon.reference)

## Set tibble of bacteria abundance
bacteria.abundance.data <- ASV.abundance.matrix %>%
  full_join(ASV.taxa.matrix, by = "taxon_id") %>%
  full_join(microbiome.tidyamplicon.reference$samples, by = "sample_id") %>%
  select(Population:Compartment, phylum:genus, abundance, rel_abundance) %>%
  rename(
    Phylum = phylum, Class = class, Order = order, Family = family, Genus = genus,
    Abundance = abundance, Relative_Abundance = rel_abundance
  )

## Set aggregated sample data
sample.data <- microbiome.tidyamplicon.reference$samples %>%
	select(Population:Compartment) %>%
	distinct()
```





\newpage
# Filter Abundances

\vspace{10pt}

```{r Filter Abundances: Pathogenic Bacteria, echo = TRUE}
## Set tibbles of abundances for different mutualistic bacteria
# Mycobacterium
mycobacterium.abundances <- bacteria.abundance.data %>%
  filter(Genus == "Mycobacterium") %>%
  select(Population, Compartment, Abundance, Relative_Abundance) %>%
  group_by(Population, Compartment) %>%
  summarise(
    Mycobacterium_Abundance = sum(Abundance),
    Mycobacterium_Relative_Abundance = sum(Relative_Abundance),
    .groups = "keep"
  )

# Legionella
legionella.abundances <- bacteria.abundance.data %>%
  filter(Genus == "Legionella") %>%
  select(Population, Compartment, Abundance, Relative_Abundance) %>%
  group_by(Population, Compartment) %>%
  summarise(
    Legionella_Abundance = sum(Abundance),
    Legionella_Relative_Abundance = sum(Relative_Abundance),
    .groups = "keep"
  )

# Staphylococcus
staphylococcus.abundances <- bacteria.abundance.data %>%
  filter(Genus == "Staphylococcus") %>%
  select(Population, Compartment, Abundance, Relative_Abundance) %>%
  group_by(Population, Compartment) %>%
  summarise(
    Staphylococcus_Abundance = sum(Abundance),
    Staphylococcus_Relative_Abundance = sum(Relative_Abundance),
    .groups = "keep"
  )

# Stenotrophomonas
stenotrophomonas.abundances <- bacteria.abundance.data %>%
  filter(Genus == "Stenotrophomonas") %>%
  select(Population, Compartment, Abundance, Relative_Abundance) %>%
  group_by(Population, Compartment) %>%
  summarise(
    Stenotrophomonas_Abundance = sum(Abundance),
    Stenotrophomonas_Relative_Abundance = sum(Relative_Abundance),
    .groups = "keep"
  )

# Acinetobacter
acinetobacter.abundances <- bacteria.abundance.data %>%
  filter(Genus == "Acinetobacter") %>%
  select(Population, Compartment, Abundance, Relative_Abundance) %>%
  group_by(Population, Compartment) %>%
  summarise(
    Acinetobacter_Abundance = sum(Abundance),
    Acinetobacter_Relative_Abundance = sum(Relative_Abundance),
    .groups = "keep"
  )

# Clostridium
clostridium.abundances <- bacteria.abundance.data %>%
  filter(Genus == "Clostridium_sensu_stricto") %>%
  select(Population, Compartment, Abundance, Relative_Abundance) %>%
  group_by(Population, Compartment) %>%
  summarise(
    Clostridium_Abundance = sum(Abundance),
    Clostridium_Relative_Abundance = sum(Relative_Abundance),
    .groups = "keep"
  )

# Paenibacillus
paenibacillus.abundances <- bacteria.abundance.data %>%
  filter(Genus == "Paenibacillus") %>%
  select(Population, Compartment, Abundance, Relative_Abundance) %>%
  group_by(Population, Compartment) %>%
  summarise(
    Paenibacillus_Abundance = sum(Abundance),
    Paenibacillus_Relative_Abundance = sum(Relative_Abundance),
    .groups = "keep"
  )

# Williamsia
williamsia.abundances <- bacteria.abundance.data %>%
  filter(Genus == "Williamsia") %>%
  select(Population, Compartment, Abundance, Relative_Abundance) %>%
  group_by(Population, Compartment) %>%
  summarise(
    Williamsia_Abundance = sum(Abundance),
    Williamsia_Relative_Abundance = sum(Relative_Abundance),
    .groups = "keep"
  )

# Sphingomonas
sphingomonas.abundances <- bacteria.abundance.data %>%
  filter(Genus == "Sphingomonas") %>%
  select(Population, Compartment, Abundance, Relative_Abundance) %>%
  group_by(Population, Compartment) %>%
  summarise(
    Sphingomonas_Abundance = sum(Abundance),
    Sphingomonas_Relative_Abundance = sum(Relative_Abundance),
    .groups = "keep"
  )

# Xanthomonas
xanthomonas.abundances <- bacteria.abundance.data %>%
  filter(Genus == "Xanthomonas") %>%
  select(Population, Compartment, Abundance, Relative_Abundance) %>%
  group_by(Population, Compartment) %>%
  summarise(
    Xanthomonas_Abundance = sum(Abundance),
    Xanthomonas_Relative_Abundance = sum(Relative_Abundance),
    .groups = "keep"
  )

# Rhizobacter
rhizobacter.abundances <- bacteria.abundance.data %>%
  filter(Genus == "Rhizobacter") %>%
  select(Population, Compartment, Abundance, Relative_Abundance) %>%
  group_by(Population, Compartment) %>%
  summarise(
    Rhizobacter_Abundance = sum(Abundance),
    Rhizobacter_Relative_Abundance = sum(Relative_Abundance),
    .groups = "keep"
  )

# Agrobacterium
agrobacterium.abundances <- bacteria.abundance.data %>%
  filter(Genus == "Agrobacterium") %>%
  select(Population, Compartment, Abundance, Relative_Abundance) %>%
  group_by(Population, Compartment) %>%
  summarise(
    Agrobacterium_Abundance = sum(Abundance),
    Agrobacterium_Relative_Abundance = sum(Relative_Abundance),
    .groups = "keep"
  )

## Combine abundances into a single tibble with urbanization metrics
pathogenic.bacteria.data <- sample.data %>%
	full_join(mycobacterium.abundances, by = c("Population", "Compartment")) %>%
	full_join(legionella.abundances, by = c("Population", "Compartment")) %>%
	full_join(staphylococcus.abundances, by = c("Population", "Compartment")) %>%
	full_join(stenotrophomonas.abundances, by = c("Population", "Compartment")) %>%
	full_join(acinetobacter.abundances, by = c("Population", "Compartment")) %>%
	full_join(clostridium.abundances, by = c("Population", "Compartment")) %>%
	full_join(paenibacillus.abundances, by = c("Population", "Compartment")) %>%
	full_join(williamsia.abundances, by = c("Population", "Compartment")) %>%
	full_join(sphingomonas.abundances, by = c("Population", "Compartment")) %>%
	full_join(xanthomonas.abundances, by = c("Population", "Compartment")) %>%
	full_join(rhizobacter.abundances, by = c("Population", "Compartment")) %>%
	full_join(agrobacterium.abundances, by = c("Population", "Compartment")) %>%
	replace(is.na(.), 0) %>%
	full_join(urbanization.data, by = "Population") %>%
	type_convert(col_types = c("ffnnnnnnnnnnnnnnnnnnnnnnnnnnnnn"))
```





\newpage
# Mycobacterium GAMs

\vspace{10pt}

```{r Mycobacterium GAMs, echo TRUE}
## Mycobacterium by distance
mycobacterium.by.distance.GAM <- gam(
	Mycobacterium_Relative_Abundance ~ Compartment
	  + s(Distance, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Mycobacterium by HII
mycobacterium.by.HII.GAM <- gam(
	Mycobacterium_Relative_Abundance ~ Compartment
	  + s(Human_Influence_Index, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Mycobacterium by ISC
mycobacterium.by.ISC.GAM <- gam(
	Mycobacterium_Relative_Abundance ~ Compartment
	  + s(Mean_ISC, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)
```

\vspace{10pt}

## Check Model Assumptions

```{r performance Diagnostics: Mycobacterium GAMs, echo = TRUE, eval = FALSE}
## Mycobacterium abundance-by-distance model diagnostics
check_model(mycobacterium.by.distance.GAM)
# Visual check = assumptions met

## Mycobacterium abundance-by-HII model diagnostics
check_model(mycobacterium.by.HII.GAM)
# Visual check = assumptions met

## Mycobacterium abundance-by-ISC model diagnostics
check_model(mycobacterium.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
## ANOVAs

\vspace{10pt}

```{r ANOVA Table: Mycobacterium Abundance-by-Distance GMM, echo = FALSE}
kable(
  tidy(mycobacterium.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Mycobacterium relative abundance-by-distance GAM. Adjusted R-squared = 0.592, deviance = 60.1 Compartment: F = 100, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Mycobacterium Abundance-by-HII GAM, echo = FALSE}
kable(
  tidy(mycobacterium.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Mycobacterium relative abundance-by-HII GAM. Adjusted R-squared = 0.589, deviance = 59.8 Compartment: F = 99.4, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Mycobacterium Abundance-by-ISC GAM, echo = FALSE}
kable(
  tidy(mycobacterium.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Mycobacterium relative abundance-by-ISC GAM. Adjusted R-squared = 0.586, deviance = 59.2 Compartment: F = 98.5, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Legionella GAMs

\vspace{10pt}

```{r Legionella GAMs, echo TRUE}
## Legionella by distance
legionella.by.distance.GAM <- gam(
	Legionella_Relative_Abundance ~ Compartment
	  + s(Distance, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Legionella by HII
legionella.by.HII.GAM <- gam(
	Legionella_Relative_Abundance ~ Compartment
	  + s(Human_Influence_Index, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Legionella by ISC
legionella.by.ISC.GAM <- gam(
	Legionella_Relative_Abundance ~ Compartment
	  + s(Mean_ISC, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)
```

\vspace{10pt}

## Check Model Assumptions

```{r performance Diagnostics: Legionella GAMs, echo = TRUE, eval = FALSE}
## Legionella abundance-by-distance model diagnostics
check_model(legionella.by.distance.GAM)
# Visual check = assumptions met

## Legionella abundance-by-HII model diagnostics
check_model(legionella.by.HII.GAM)
# Visual check = assumptions met

## Legionella abundance-by-ISC model diagnostics
check_model(legionella.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
## ANOVAs

\vspace{10pt}

```{r ANOVA Table: Legionella Abundance-by-Distance GMM, echo = FALSE}
kable(
  tidy(legionella.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Legionella relative abundance-by-distance GAM. Adjusted R-squared = 0.481, deviance = 49.4 Compartment: F = 62.6, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Legionella Abundance-by-HII GAM, echo = FALSE}
kable(
  tidy(legionella.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Legionella relative abundance-by-HII GAM. Adjusted R-squared = 0.479, deviance = 49.2 Compartment: F = 62.4, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Legionella Abundance-by-ISC GAM, echo = FALSE}
kable(
  tidy(legionella.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Legionella relative abundance-by-ISC GAM. Adjusted R-squared = 0.478, deviance = 49.1 Compartment: F = 62.3, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```




\newpage
# Staphylococcus GAMs

\vspace{10pt}

```{r Staphylococcus GAMs, echo TRUE}
## Staphylococcus by distance
staphylococcus.by.distance.GAM <- gam(
	Staphylococcus_Relative_Abundance ~ Compartment
	  + s(Distance, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Staphylococcus by HII
staphylococcus.by.HII.GAM <- gam(
	Staphylococcus_Relative_Abundance ~ Compartment
	  + s(Human_Influence_Index, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Staphylococcus by ISC
staphylococcus.by.ISC.GAM <- gam(
	Staphylococcus_Relative_Abundance ~ Compartment
	  + s(Mean_ISC, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)
```

\vspace{10pt}

## Check Model Assumptions

```{r performance Diagnostics: Staphylococcus GAMs, echo = TRUE, eval = FALSE}
## Staphylococcus abundance-by-distance model diagnostics
check_model(staphylococcus.by.distance.GAM)
# Visual check = assumptions met

## Staphylococcus abundance-by-HII model diagnostics
check_model(staphylococcus.by.HII.GAM)
# Visual check = assumptions met

## Staphylococcus abundance-by-ISC model diagnostics
check_model(staphylococcus.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
## ANOVAs

\vspace{10pt}

```{r ANOVA Table: Staphylococcus Abundance-by-Distance GMM, echo = FALSE}
kable(
  tidy(staphylococcus.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Staphylococcus relative abundance-by-distance GAM. Adjusted R-squared = 0.117, deviance = 15.4 Compartment: F = 1.836, P = 0.180.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Staphylococcus Abundance-by-HII GAM, echo = FALSE}
kable(
  tidy(staphylococcus.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Staphylococcus relative abundance-by-HII GAM. Adjusted R-squared = 0.403, deviance = 44.2 Compartment: F = 2.717, P = 0.104.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Staphylococcus Abundance-by-ISC GAM, echo = FALSE}
kable(
  tidy(staphylococcus.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Staphylococcus relative abundance-by-ISC GAM. Adjusted R-squared = 0.023, deviance = 5.1 Compartment: F = 1.67, P = 0.201.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```






\newpage
# Stenotrophomonas GAMs

\vspace{10pt}

```{r Stenotrophomonas GAMs, echo TRUE}
## Stenotrophomonas by distance
stenotrophomonas.by.distance.GAM <- gam(
	Stenotrophomonas_Relative_Abundance ~ Compartment
	  + s(Distance, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Stenotrophomonas by HII
stenotrophomonas.by.HII.GAM <- gam(
	Stenotrophomonas_Relative_Abundance ~ Compartment
	  + s(Human_Influence_Index, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Stenotrophomonas by ISC
stenotrophomonas.by.ISC.GAM <- gam(
	Stenotrophomonas_Relative_Abundance ~ Compartment
	  + s(Mean_ISC, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)
```

\vspace{10pt}

## Check Model Assumptions

```{r performance Diagnostics: Stenotrophomonas GAMs, echo = TRUE, eval = FALSE}
## Stenotrophomonas abundance-by-distance model diagnostics
check_model(stenotrophomonas.by.distance.GAM)
# Visual check = assumptions met

## Stenotrophomonas abundance-by-HII model diagnostics
check_model(stenotrophomonas.by.HII.GAM)
# Visual check = assumptions met

## Stenotrophomonas abundance-by-ISC model diagnostics
check_model(stenotrophomonas.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
## ANOVAs

\vspace{10pt}

```{r ANOVA Table: Stenotrophomonas Abundance-by-Distance GMM, echo = FALSE}
kable(
  tidy(stenotrophomonas.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Stenotrophomonas relative abundance-by-distance GAM. Adjusted R-squared = 0.257, deviance = 27.6 Compartment: F = 21.2, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Stenotrophomonas Abundance-by-HII GAM, echo = FALSE}
kable(
  tidy(stenotrophomonas.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Stenotrophomonas relative abundance-by-HII GAM. Adjusted R-squared = 0.225, deviance = 24.1 Compartment: F = 20.3, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Stenotrophomonas Abundance-by-ISC GAM, echo = FALSE}
kable(
  tidy(stenotrophomonas.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Stenotrophomonas relative abundance-by-ISC GAM. Adjusted R-squared = 0.242, deviance = 26.1 Compartment: F = 20.8, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Acinetobacter GAMs

\vspace{10pt}

```{r Acinetobacter GAMs, echo TRUE}
## Acinetobacter by distance
acinetobacter.by.distance.GAM <- gam(
	Acinetobacter_Relative_Abundance ~ Compartment
	  + s(Distance, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Acinetobacter by HII
acinetobacter.by.HII.GAM <- gam(
	Acinetobacter_Relative_Abundance ~ Compartment
	  + s(Human_Influence_Index, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Acinetobacter by ISC
acinetobacter.by.ISC.GAM <- gam(
	Acinetobacter_Relative_Abundance ~ Compartment
	  + s(Mean_ISC, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)
```

\vspace{10pt}

## Check Model Assumptions

```{r performance Diagnostics: Acinetobacter GAMs, echo = TRUE, eval = FALSE}
## Acinetobacter abundance-by-distance model diagnostics
check_model(acinetobacter.by.distance.GAM)
# Visual check = assumptions met

## Acinetobacter abundance-by-HII model diagnostics
check_model(acinetobacter.by.HII.GAM)
# Visual check = assumptions met

## Acinetobacter abundance-by-ISC model diagnostics
check_model(acinetobacter.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
## ANOVAs

\vspace{10pt}

```{r ANOVA Table: Acinetobacter Abundance-by-Distance GMM, echo = FALSE}
kable(
  tidy(acinetobacter.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Acinetobacter relative abundance-by-distance GAM. Adjusted R-squared = 0.089, deviance = 11.4 Compartment: F = 2.542, P = 0.116.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Acinetobacter Abundance-by-HII GAM, echo = FALSE}
kable(
  tidy(acinetobacter.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Acinetobacter relative abundance-by-HII GAM. Adjusted R-squared = 0.028, deviance = 4.8 Compartment: F = 2.381, P = 0.127.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Acinetobacter Abundance-by-ISC GAM, echo = FALSE}
kable(
  tidy(acinetobacter.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Acinetobacter relative abundance-by-ISC GAM. Adjusted R-squared = 0.065, deviance = 8.9 Compartment: F = 2.476, P = 0.120.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Clostridium GAMs

\vspace{10pt}

```{r Clostridium GAMs, echo TRUE}
## Clostridium by distance
clostridium.by.distance.GAM <- gam(
	Clostridium_Relative_Abundance ~ Compartment
	  + s(Distance, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Clostridium by HII
clostridium.by.HII.GAM <- gam(
	Clostridium_Relative_Abundance ~ Compartment
	  + s(Human_Influence_Index, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Clostridium by ISC
clostridium.by.ISC.GAM <- gam(
	Clostridium_Relative_Abundance ~ Compartment
	  + s(Mean_ISC, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)
```

\vspace{10pt}

## Check Model Assumptions

```{r performance Diagnostics: Clostridium GAMs, echo = TRUE, eval = FALSE}
## Clostridium abundance-by-distance model diagnostics
check_model(clostridium.by.distance.GAM)
# Visual check = assumptions met

## Clostridium abundance-by-HII model diagnostics
check_model(clostridium.by.HII.GAM)
# Visual check = assumptions met

## Clostridium abundance-by-ISC model diagnostics
check_model(clostridium.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
## ANOVAs

\vspace{10pt}

```{r ANOVA Table: Clostridium Abundance-by-Distance GMM, echo = FALSE}
kable(
  tidy(clostridium.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Clostridium relative abundance-by-distance GAM. Adjusted R-squared = 0.520, deviance = 53.4 Compartment: F = 68.9, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Clostridium Abundance-by-HII GAM, echo = FALSE}
kable(
  tidy(clostridium.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Clostridium relative abundance-by-HII GAM. Adjusted R-squared = 0.479, deviance = 49.0 Compartment: F = 63.4, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Clostridium Abundance-by-ISC GAM, echo = FALSE}
kable(
  tidy(clostridium.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Clostridium relative abundance-by-ISC GAM. Adjusted R-squared = 0.506, deviance = 51.9 Compartment: F = 66.85, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Paenibacillus GAMs

\vspace{10pt}

```{r Paenibacillus GAMs, echo TRUE}
## Paenibacillus by distance
paenibacillus.by.distance.GAM <- gam(
	Paenibacillus_Relative_Abundance ~ Compartment
	  + s(Distance, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Paenibacillus by HII
paenibacillus.by.HII.GAM <- gam(
	Paenibacillus_Relative_Abundance ~ Compartment
	  + s(Human_Influence_Index, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Paenibacillus by ISC
paenibacillus.by.ISC.GAM <- gam(
	Paenibacillus_Relative_Abundance ~ Compartment
	  + s(Mean_ISC, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)
```

\vspace{10pt}

## Check Model Assumptions

```{r performance Diagnostics: Paenibacillus GAMs, echo = TRUE, eval = FALSE}
## Paenibacillus abundance-by-distance model diagnostics
check_model(paenibacillus.by.distance.GAM)
# Visual check = assumptions met

## Paenibacillus abundance-by-HII model diagnostics
check_model(paenibacillus.by.HII.GAM)
# Visual check = assumptions met

## Paenibacillus abundance-by-ISC model diagnostics
check_model(paenibacillus.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
## ANOVAs

\vspace{10pt}

```{r ANOVA Table: Paenibacillus Abundance-by-Distance GMM, echo = FALSE}
kable(
  tidy(paenibacillus.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Paenibacillus relative abundance-by-distance GAM. Adjusted R-squared = 0.396, deviance = 41.3 Compartment: F = 39.78, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Paenibacillus Abundance-by-HII GAM, echo = FALSE}
kable(
  tidy(paenibacillus.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Paenibacillus relative abundance-by-HII GAM. Adjusted R-squared = 0.388, deviance = 40.9 Compartment: F = 39.21, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Paenibacillus Abundance-by-ISC GAM, echo = FALSE}
kable(
  tidy(paenibacillus.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Paenibacillus relative abundance-by-ISC GAM. Adjusted R-squared = 0.349, deviance = 36.3 Compartment: F = 36.87, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Williamsia GAMs

\vspace{10pt}

```{r Williamsia GAMs, echo TRUE}
## Williamsia by distance
williamsia.by.distance.GAM <- gam(
	Williamsia_Relative_Abundance ~ Compartment
	  + s(Distance, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Williamsia by HII
williamsia.by.HII.GAM <- gam(
	Williamsia_Relative_Abundance ~ Compartment
	  + s(Human_Influence_Index, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Williamsia by ISC
williamsia.by.ISC.GAM <- gam(
	Williamsia_Relative_Abundance ~ Compartment
	  + s(Mean_ISC, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)
```

\vspace{10pt}

## Check Model Assumptions

```{r performance Diagnostics: Williamsia GAMs, echo = TRUE, eval = FALSE}
## Williamsia abundance-by-distance model diagnostics
check_model(williamsia.by.distance.GAM)
# Visual check = assumptions met

## Williamsia abundance-by-HII model diagnostics
check_model(williamsia.by.HII.GAM)
# Visual check = assumptions met

## Williamsia abundance-by-ISC model diagnostics
check_model(williamsia.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
## ANOVAs

\vspace{10pt}

```{r ANOVA Table: Williamsia Abundance-by-Distance GMM, echo = FALSE}
kable(
  tidy(williamsia.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Williamsia relative abundance-by-distance GAM. Adjusted R-squared = 0.038, deviance = 6.24 Compartment: F = 0.914, P = 0.342.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Williamsia Abundance-by-HII GAM, echo = FALSE}
kable(
  tidy(williamsia.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Williamsia relative abundance-by-HII GAM. Adjusted R-squared = 0.044, deviance = 6.83 Compartment: F = 0.920, P = 0.341.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Williamsia Abundance-by-ISC GAM, echo = FALSE}
kable(
  tidy(williamsia.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Williamsia relative abundance-by-ISC GAM. Adjusted R-squared = 0.023, deviance = 4.64 Compartment: F = 0.901, P = 0.346.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Sphingomonas GAMs

\vspace{10pt}

```{r Sphingomonas GAMs, echo TRUE}
## Sphingomonas by distance
sphingomonas.by.distance.GAM <- gam(
	Sphingomonas_Relative_Abundance ~ Compartment
	  + s(Distance, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Sphingomonas by HII
sphingomonas.by.HII.GAM <- gam(
	Sphingomonas_Relative_Abundance ~ Compartment
	  + s(Human_Influence_Index, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Sphingomonas by ISC
sphingomonas.by.ISC.GAM <- gam(
	Sphingomonas_Relative_Abundance ~ Compartment
	  + s(Mean_ISC, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)
```

\vspace{10pt}

## Check Model Assumptions

```{r performance Diagnostics: Sphingomonas GAMs, echo = TRUE, eval = FALSE}
## Sphingomonas abundance-by-distance model diagnostics
check_model(sphingomonas.by.distance.GAM)
# Visual check = assumptions met

## Sphingomonas abundance-by-HII model diagnostics
check_model(sphingomonas.by.HII.GAM)
# Visual check = assumptions met

## Sphingomonas abundance-by-ISC model diagnostics
check_model(sphingomonas.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
## ANOVAs

\vspace{10pt}

```{r ANOVA Table: Sphingomonas Abundance-by-Distance GMM, echo = FALSE}
kable(
  tidy(sphingomonas.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Sphingomonas relative abundance-by-distance GAM. Adjusted R-squared = 0.584, deviance = 60.4 Compartment: F = 76.42, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Sphingomonas Abundance-by-HII GAM, echo = FALSE}
kable(
  tidy(sphingomonas.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Sphingomonas relative abundance-by-HII GAM. Adjusted R-squared = 0.453, deviance = 46.1 Compartment: F = 58.2, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Sphingomonas Abundance-by-ISC GAM, echo = FALSE}
kable(
  tidy(sphingomonas.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Sphingomonas relative abundance-by-ISC GAM. Adjusted R-squared = 0.453, deviance = 46.1 Compartment: F = 58.2, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Xanthomonas GAMs

\vspace{10pt}

```{r Xanthomonas GAMs, echo TRUE}
## Xanthomonas by distance
xanthomonas.by.distance.GAM <- gam(
	Xanthomonas_Relative_Abundance ~ Compartment
	  + s(Distance, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Xanthomonas by HII
xanthomonas.by.HII.GAM <- gam(
	Xanthomonas_Relative_Abundance ~ Compartment
	  + s(Human_Influence_Index, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Xanthomonas by ISC
xanthomonas.by.ISC.GAM <- gam(
	Xanthomonas_Relative_Abundance ~ Compartment
	  + s(Mean_ISC, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)
```

\vspace{10pt}

## Check Model Assumptions

```{r performance Diagnostics: Xanthomonas GAMs, echo = TRUE, eval = FALSE}
## Xanthomonas abundance-by-distance model diagnostics
check_model(xanthomonas.by.distance.GAM)
# Visual check = assumptions met

## Xanthomonas abundance-by-HII model diagnostics
check_model(xanthomonas.by.HII.GAM)
# Visual check = assumptions met

## Xanthomonas abundance-by-ISC model diagnostics
check_model(xanthomonas.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
## ANOVAs

\vspace{10pt}

```{r ANOVA Table: Xanthomonas Abundance-by-Distance GMM, echo = FALSE}
kable(
  tidy(xanthomonas.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Xanthomonas relative abundance-by-distance GAM. Adjusted R-squared = 0.251, deviance = 27.1 Compartment: F = 18.21, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Xanthomonas Abundance-by-HII GAM, echo = FALSE}
kable(
  tidy(xanthomonas.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Xanthomonas relative abundance-by-HII GAM. Adjusted R-squared = 0.306, deviance = 32.5 Compartment: F = 19.64, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Xanthomonas Abundance-by-ISC GAM, echo = FALSE}
kable(
  tidy(xanthomonas.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Xanthomonas relative abundance-by-ISC GAM. Adjusted R-squared = 0.234, deviance = 25.5 Compartment: F = 17.82, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Rhizobacter GAMs

\vspace{10pt}

```{r Rhizobacter GAMs, echo TRUE}
## Rhizobacter by distance
rhizobacter.by.distance.GAM <- gam(
	Rhizobacter_Relative_Abundance ~ Compartment
	  + s(Distance, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Rhizobacter by HII
rhizobacter.by.HII.GAM <- gam(
	Rhizobacter_Relative_Abundance ~ Compartment
	  + s(Human_Influence_Index, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Rhizobacter by ISC
rhizobacter.by.ISC.GAM <- gam(
	Rhizobacter_Relative_Abundance ~ Compartment
	  + s(Mean_ISC, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)
```

\vspace{10pt}

## Check Model Assumptions

```{r performance Diagnostics: Rhizobacter GAMs, echo = TRUE, eval = FALSE}
## Rhizobacter abundance-by-distance model diagnostics
check_model(rhizobacter.by.distance.GAM)
# Visual check = assumptions met

## Rhizobacter abundance-by-HII model diagnostics
check_model(rhizobacter.by.HII.GAM)
# Visual check = assumptions met

## Rhizobacter abundance-by-ISC model diagnostics
check_model(rhizobacter.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
## ANOVAs

\vspace{10pt}

```{r ANOVA Table: Rhizobacter Abundance-by-Distance GMM, echo = FALSE}
kable(
  tidy(rhizobacter.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Rhizobacter relative abundance-by-distance GAM. Adjusted R-squared = 0.653, deviance = 67.6 Compartment: F = 115.9, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Rhizobacter Abundance-by-HII GAM, echo = FALSE}
kable(
  tidy(rhizobacter.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Rhizobacter relative abundance-by-HII GAM. Adjusted R-squared = 0.589, deviance = 59.9 Compartment: F = 97.81, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Rhizobacter Abundance-by-ISC GAM, echo = FALSE}
kable(
  tidy(rhizobacter.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Rhizobacter relative abundance-by-ISC GAM. Adjusted R-squared = 0.587, deviance = 59.7 Compartment: F = 97.38, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Agrobacterium GAMs

\vspace{10pt}

```{r Agrobacterium GAMs, echo TRUE}
## Agrobacterium by distance
agrobacterium.by.distance.GAM <- gam(
	Agrobacterium_Relative_Abundance ~ Compartment
	  + s(Distance, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Agrobacterium by HII
agrobacterium.by.HII.GAM <- gam(
	Agrobacterium_Relative_Abundance ~ Compartment
	  + s(Human_Influence_Index, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)

## Agrobacterium by ISC
agrobacterium.by.ISC.GAM <- gam(
	Agrobacterium_Relative_Abundance ~ Compartment
	  + s(Mean_ISC, by = Compartment, bs = "ts", k = 10),
	data = pathogenic.bacteria.data,
	method = "REML"
)
```

\vspace{10pt}

## Check Model Assumptions

```{r performance Diagnostics: Agrobacterium GAMs, echo = TRUE, eval = FALSE}
## Agrobacterium abundance-by-distance model diagnostics
check_model(agrobacterium.by.distance.GAM)
# Visual check = assumptions met

## Agrobacterium abundance-by-HII model diagnostics
check_model(agrobacterium.by.HII.GAM)
# Visual check = assumptions met

## Agrobacterium abundance-by-ISC model diagnostics
check_model(agrobacterium.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
## ANOVAs

\vspace{10pt}

```{r ANOVA Table: Agrobacterium Abundance-by-Distance GMM, echo = FALSE}
kable(
  tidy(agrobacterium.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Agrobacterium relative abundance-by-distance GAM. Adjusted R-squared = 0.539, deviance = 56.4 Compartment: F = 59.84, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Agrobacterium Abundance-by-HII GAM, echo = FALSE}
kable(
  tidy(agrobacterium.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Agrobacterium relative abundance-by-HII GAM. Adjusted R-squared = 0.692, deviance = 71.8 Compartment: F = 89.55, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Agrobacterium Abundance-by-ISC GAM, echo = FALSE}
kable(
  tidy(agrobacterium.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the Agrobacterium relative abundance-by-ISC GAM. Adjusted R-squared = 0.474, deviance = 49.9 Compartment: F = 52.36, P < 0.001.",
  col.names = c("Term", "EDF", "Ref. df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```










\newpage
# Export Data

```{r Export Data, echo = TRUE}
## Pathogenic bacteria
write_rds(
	pathogenic.bacteria.data,
	file = "data/pathogenic_bacteria_data.rds"
)
```

\vspace{10pt}

```{r Save Workspace, echo = TRUE}
save.image("data_analysis/10-bacterial_functional_groups/pathogenic_bacteria-workspace.RData")
```










\newpage
# R Session Information

```{r R Packages, echo = FALSE}
df_session_packages <- devtools::session_info()$packages %>%
  as.data.frame(.) %>%
  filter(attached == TRUE) %>%
  dplyr::select(loadedversion, date) %>%
  rownames_to_column()

colnames(df_session_packages) <- c("Package", "Loaded Version", "Date")

kable(
  df_session_packages,
  booktabs = TRUE,
  caption = "Packages required for data management and analysis."
) %>%
  kable_styling(
    full_width = FALSE,
    latex_options = c("HOLD_position", "striped")
  )
```
