---
title: "TRhizo-urbanMicrobiome"
subtitle: "Carbon & Nitrogen Analyses"
author: "David Murray-Stoker"
output:
  pdf_document:
    toc: true
    toc_depth: 5
    fig_caption: yes
    latex_engine: xelatex
always_allow_html: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(results = "hold", fig.pos = "H", fig.align = "center", out.width = "92.5%")
options(knitr.graphics.error = FALSE)
kableExtra::usepackage_latex("float")
```

```{r Load Packages for R Markdown, include = FALSE}
library(kableExtra)
library(knitr)
```





\newpage
# Load Packages

\vspace{10pt}

```{r Load Packages, include = FALSE}
## Load the tidyverse
library(tidyverse)

## Packages for analyses
library(broom)
library(easystats)
library(mgcv)

## Set contrasts for Type III sums-of-squares
options(contrasts = c("contr.sum", "contr.sum"))

## Make the results reproducible
set.seed(666)
```





\newpage
# Data Management

\vspace{10pt}

```{r Load Data, echo = TRUE}
## Load the carbon data
carbon.data.uncleaned <- read_csv(
	file = "data/urbanMicrobiome-carbon_data.csv",
	col_types = c("fnnnn"),
	show_col_types = FALSE
)

## Load the nitrogen data
nitrogen.data.uncleaned <- read_csv(
	file = "data/urbanMicrobiome-nitrogen_data.csv",
	col_types = c("fnnnn"),
	show_col_types = FALSE
)

## Load the urbanization data
urbanization.data <- read_rds(
	file = "data/urbanization_data.rds"
)
```

\vspace{10pt}

```{r Merge Nutrient and Urbanization Metric Data, echo = TRUE}
## Combined data
carbon.nitrogen.data <- urbanization.data %>%
	full_join(carbon.data.uncleaned, by = "Population") %>%
	full_join(nitrogen.data.uncleaned, by = "Population")
```





\newpage
# Carbon Analyses 

\vspace{10pt}

## Soil Total Carbon

### Fit the GAMs

\vspace{10pt}

```{r Soil Total Carbon GAMs, echo TRUE}
## Soil total carbon
# Distance
soil.total.C.by.distance.GAM <- gam(
	Soil_Total_Carbon ~ s(Distance, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# HII
soil.total.C.by.HII.GAM <- gam(
	Soil_Total_Carbon ~ s(Human_Influence_Index, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# ISC
soil.total.C.by.ISC.GAM <- gam(
	Soil_Total_Carbon ~ s(Mean_ISC, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Soil Total Carbon GAMs, echo = TRUE, eval = FALSE}
## Soil total carbon-by-distance model diagnostics
check_model(soil.total.C.by.distance.GAM)
# Visual check = assumptions met

## Soil total carbon-by-HII model diagnostics
check_model(soil.total.C.by.HII.GAM)
# Visual check = assumptions met

## Soil total carbon-by-ISC model diagnostics
check_model(soil.total.C.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
### ANOVAs

\vspace{10pt}

```{r ANOVA Table: Soil Total Carbon-by-Distance GAM, echo = FALSE}
kable(
  tidy(soil.total.C.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the soil total carbon-by-distance GAM. Adjusted R-squared = 0.298, deviance = 35.0.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Soil Total Carbon-by-HII GAM, echo = FALSE}
kable(
  tidy(soil.total.C.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the soil total carbon-by-HII GAM. Adjusted R-squared = 0.152, deviance = 17.4.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Soil Total Carbon-by-ISC GAM, echo = FALSE}
kable(
  tidy(soil.total.C.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the soil total carbon-by-ISC GAM. Adjusted R-squared = 0.331, deviance = 37.9.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Leaf Total Carbon

### Fit the GAMs

\vspace{10pt}

```{r Leaf Total Carbon GAMs, echo TRUE}
## Leaf total carbon
# Distance
leaf.total.C.by.distance.GAM <- gam(
	Leaf_Total_Carbon ~ s(Distance, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# HII
leaf.total.C.by.HII.GAM <- gam(
	Leaf_Total_Carbon ~ s(Human_Influence_Index, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# ISC
leaf.total.C.by.ISC.GAM <- gam(
	Leaf_Total_Carbon ~ s(Mean_ISC, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Leaf Total Carbon GAMs, echo = TRUE, eval = FALSE}
## Leaf total carbon-by-distance model diagnostics
check_model(leaf.total.C.by.distance.GAM)
# Visual check = assumptions met

## Leaf total carbon-by-HII model diagnostics
check_model(leaf.total.C.by.HII.GAM)
# Visual check = assumptions met

## Leaf total carbon-by-ISC model diagnostics
check_model(leaf.total.C.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
### ANOVAs

\vspace{10pt}

```{r ANOVA Table: Leaf Total Carbon-by-Distance GAM, echo = FALSE}
kable(
  tidy(leaf.total.C.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the leaf total carbon-by-distance GAM. Adjusted R-squared < 0.001, deviance = 0.001.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Leaf Total Carbon-by-HII GAM, echo = FALSE}
kable(
  tidy(leaf.total.C.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the leaf total carbon-by-HII GAM. Adjusted R-squared < 0.001, deviance < 0.001.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Leaf Total Carbon-by-ISC GAM, echo = FALSE}
kable(
  tidy(leaf.total.C.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the leaf total carbon-by-ISC GAM. Adjusted R-squared = 0.188, deviance = 23.2.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Soil Delta 13C

### Fit the GAMs

\vspace{10pt}

```{r Soil Delta 13C GAMs, echo TRUE}
## Soil delta 13C
# Distance
soil.delta.13C.by.distance.GAM <- gam(
	Soil_Delta_13C ~ s(Distance, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# HII
soil.delta.13C.by.HII.GAM <- gam(
	Soil_Delta_13C ~ s(Human_Influence_Index, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# ISC
soil.delta.13C.by.ISC.GAM <- gam(
	Soil_Delta_13C ~ s(Mean_ISC, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Soil Delta 13C GAMs, echo = TRUE, eval = FALSE}
## Soil delta 13C-by-distance model diagnostics
check_model(soil.delta.13C.by.distance.GAM)
# Visual check = assumptions met

## Soil delta 13C-by-HII model diagnostics
check_model(soil.delta.13C.by.HII.GAM)
# Visual check = assumptions met

## Soil delta 13C-by-ISC model diagnostics
check_model(soil.delta.13C.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
### ANOVAs

\vspace{10pt}

```{r ANOVA Table: Soil Delta 13C-by-Distance GAM, echo = FALSE}
kable(
  tidy(soil.delta.13C.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the soil delta 13C-by-distance GAM. Adjusted R-squared = 0.362, deviance = 38.1.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Soil Delta 13C-by-HII GAM, echo = FALSE}
kable(
  tidy(soil.delta.13C.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the soil delta 13C-by-HII GAM. Adjusted R-squared = 0.216, deviance = 23.7.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Soil Delta 13C-by-ISC GAM, echo = FALSE}
kable(
  tidy(soil.delta.13C.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the soil delta 13C-by-ISC GAM. Adjusted R-squared = 0.202, deviance = 22.4.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Leaf Delta 13C

### Fit the GAMs

\vspace{10pt}

```{r Leaf Delta 13C GAMs, echo TRUE}
## Leaf delta 13C
# Distance
leaf.delta.13C.by.distance.GAM <- gam(
	Leaf_Delta_13C ~ s(Distance, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# HII
leaf.delta.13C.by.HII.GAM <- gam(
	Leaf_Delta_13C ~ s(Human_Influence_Index, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# ISC
leaf.delta.13C.by.ISC.GAM <- gam(
	Leaf_Delta_13C ~ s(Mean_ISC, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Leaf Delta 13C GAMs, echo = TRUE, eval = FALSE}
## Leaf delta 13C-by-distance model diagnostics
check_model(leaf.delta.13C.by.distance.GAM)
# Visual check = assumptions met

## Leaf delta 13C-by-HII model diagnostics
check_model(leaf.delta.13C.by.HII.GAM)
# Visual check = assumptions met

## Leaf delta 13C-by-ISC model diagnostics
check_model(leaf.delta.13C.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
### ANOVAs

\vspace{10pt}

```{r ANOVA Table: Leaf Delta 13C-by-Distance GAM, echo = FALSE}
kable(
  tidy(leaf.delta.13C.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the leaf delta 13C-by-distance GAM. Adjusted R-squared = 0.069, deviance = 8.9.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Leaf Delta 13C-by-HII GAM, echo = FALSE}
kable(
  tidy(leaf.delta.13C.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the leaf delta 13C-by-HII GAM. Adjusted R-squared = 0.011, deviance = 1.9.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Leaf Delta 13C-by-ISC GAM, echo = FALSE}
kable(
  tidy(leaf.delta.13C.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the leaf delta 13C-by-ISC GAM. Adjusted R-squared = 0.023, deviance = 3.5.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```










\newpage
# Nitrogen Analyses 

\vspace{10pt}

## Soil Total Nitrogen

### Fit the GAMs

\vspace{10pt}

```{r Soil Total Nitrogen GAMs, echo TRUE}
## Soil total carbon
# Distance
soil.total.N.by.distance.GAM <- gam(
	Soil_Total_Nitrogen ~ s(Distance, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# HII
soil.total.N.by.HII.GAM <- gam(
	Soil_Total_Nitrogen ~ s(Human_Influence_Index, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# ISC
soil.total.N.by.ISC.GAM <- gam(
	Soil_Total_Nitrogen ~ s(Mean_ISC, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Soil Total Nitrogen GAMs, echo = TRUE, eval = FALSE}
## Soil total carbon-by-distance model diagnostics
check_model(soil.total.N.by.distance.GAM)
# Visual check = assumptions met

## Soil total carbon-by-HII model diagnostics
check_model(soil.total.N.by.HII.GAM)
# Visual check = assumptions met

## Soil total carbon-by-ISC model diagnostics
check_model(soil.total.N.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
### ANOVAs

\vspace{10pt}

```{r ANOVA Table: Soil Total Nitrogen-by-Distance GAM, echo = FALSE}
kable(
  tidy(soil.total.N.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the soil total nitrogen-by-distance GAM. Adjusted R-squared = 0.126, deviance = 14.8.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Soil Total Nitrogen-by-HII GAM, echo = FALSE}
kable(
  tidy(soil.total.N.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the soil total nitrogen-by-HII GAM. Adjusted R-squared = 0.006, deviance = 1.2.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Soil Total Nitrogen-by-ISC GAM, echo = FALSE}
kable(
  tidy(soil.total.N.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the soil total nitrogen-by-ISC GAM. Adjusted R-squared = 0.036, deviance = 5.2.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Leaf Total Nitrogen

### Fit the GAMs

\vspace{10pt}

```{r Leaf Total Nitrogen GAMs, echo TRUE}
## Leaf total carbon
# Distance
leaf.total.N.by.distance.GAM <- gam(
	Leaf_Total_Nitrogen ~ s(Distance, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# HII
leaf.total.N.by.HII.GAM <- gam(
	Leaf_Total_Nitrogen ~ s(Human_Influence_Index, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# ISC
leaf.total.N.by.ISC.GAM <- gam(
	Leaf_Total_Nitrogen ~ s(Mean_ISC, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Leaf Total Nitrogen GAMs, echo = TRUE, eval = FALSE}
## Leaf total carbon-by-distance model diagnostics
check_model(leaf.total.N.by.distance.GAM)
# Visual check = assumptions met

## Leaf total carbon-by-HII model diagnostics
check_model(leaf.total.N.by.HII.GAM)
# Visual check = assumptions met

## Leaf total carbon-by-ISC model diagnostics
check_model(leaf.total.N.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
### ANOVAs

\vspace{10pt}

```{r ANOVA Table: Leaf Total Nitrogen-by-Distance GAM, echo = FALSE}
kable(
  tidy(leaf.total.N.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the leaf total nitrogen-by-distance GAM. Adjusted R-squared = 0.448, deviance = 49.8.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Leaf Total Nitrogen-by-HII GAM, echo = FALSE}
kable(
  tidy(leaf.total.N.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the leaf total nitrogen-by-HII GAM. Adjusted R-squared = 0.008, deviance = 1.4.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Leaf Total Nitrogen-by-ISC GAM, echo = FALSE}
kable(
  tidy(leaf.total.N.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the leaf total nitrogen-by-ISC GAM. Adjusted R-squared = 0.265, deviance = 30.7.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Soil Delta 15N

### Fit the GAMs

\vspace{10pt}

```{r Soil Delta 15N GAMs, echo TRUE}
## Soil delta 15N
# Distance
soil.delta.15N.by.distance.GAM <- gam(
	Soil_Delta_15N ~ s(Distance, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# HII
soil.delta.15N.by.HII.GAM <- gam(
	Soil_Delta_15N ~ s(Human_Influence_Index, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# ISC
soil.delta.15N.by.ISC.GAM <- gam(
	Soil_Delta_15N ~ s(Mean_ISC, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Soil Delta 15N GAMs, echo = TRUE, eval = FALSE}
## Soil delta 15N-by-distance model diagnostics
check_model(soil.delta.15N.by.distance.GAM)
# Visual check = assumptions met

## Soil delta 15N-by-HII model diagnostics
check_model(soil.delta.15N.by.HII.GAM)
# Visual check = assumptions met

## Soil delta 15N-by-ISC model diagnostics
check_model(soil.delta.15N.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
### ANOVAs

\vspace{10pt}

```{r ANOVA Table: Soil Delta 15N-by-Distance GAM, echo = FALSE}
kable(
  tidy(soil.delta.15N.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the soil delta 15N-by-distance GAM. Adjusted R-squared = 0.257, deviance = 27.8.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Soil Delta 15N-by-HII GAM, echo = FALSE}
kable(
  tidy(soil.delta.15N.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the soil delta 15N-by-HII GAM. Adjusted R-squared = 0.216, deviance = 23.7.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Soil Delta 15N-by-ISC GAM, echo = FALSE}
kable(
  tidy(soil.delta.15N.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the soil delta 15N-by-ISC GAM. Adjusted R-squared = 0.240, deviance = 26.1.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Leaf Delta 15N

### Fit the GAMs

\vspace{10pt}

```{r Leaf Delta 15N GAMs, echo TRUE}
## Leaf delta 15N
# Distance
leaf.delta.15N.by.distance.GAM <- gam(
	Leaf_Delta_15N ~ s(Distance, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# HII
leaf.delta.15N.by.HII.GAM <- gam(
	Leaf_Delta_15N ~ s(Human_Influence_Index, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
# ISC
leaf.delta.15N.by.ISC.GAM <- gam(
	Leaf_Delta_15N ~ s(Mean_ISC, bs = "ts", k = 10),
	data = carbon.nitrogen.data,
	method = "REML"
)
```

\vspace{10pt}

### Check Model Assumptions

```{r performance Diagnostics: Leaf Delta 15N GAMs, echo = TRUE, eval = FALSE}
## Leaf delta 15N-by-distance model diagnostics
check_model(leaf.delta.15N.by.distance.GAM)
# Visual check = assumptions met

## Leaf delta 15N-by-HII model diagnostics
check_model(leaf.delta.15N.by.HII.GAM)
# Visual check = assumptions met

## Leaf delta 15N-by-ISC model diagnostics
check_model(leaf.delta.15N.by.ISC.GAM)
# Visual check = assumptions met
```



\newpage
### ANOVAs

\vspace{10pt}

```{r ANOVA Table: Leaf Delta 15N-by-Distance GAM, echo = FALSE}
kable(
  tidy(leaf.delta.15N.by.distance.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the leaf delta 15N-by-distance GAM. Adjusted R-squared = 0.023, deviance = 3.6.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Leaf Delta 15N-by-HII GAM, echo = FALSE}
kable(
  tidy(leaf.delta.15N.by.HII.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the leaf delta 15N-by-HII GAM. Adjusted R-squared = 0.007, deviance = 1.3.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r ANOVA Table: Leaf Delta 15N-by-ISC GAM, echo = FALSE}
kable(
  tidy(leaf.delta.15N.by.ISC.GAM),
  booktabs = TRUE,
  digits = 3,
  caption = "ANOVA table for the leaf delta 15N-by-ISC GAM. Adjusted R-squared = 0.033, deviance = 4.8.",
  col.names = c("Term", "EDF", "Ref.df", "F", "P-value")
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```










\newpage
# Save the workspace

\vspace{10pt}

```{r Save Workspace, include = FALSE}
save.image("data_analysis/6-carbon_nitrogen_analyses/carbon_nitrogen-workspace.RData")
```

\vspace{10pt}

# R Session Information

```{r R Packages, echo = FALSE}
df_session_packages <- devtools::session_info()$packages %>%
  as.data.frame(.) %>%
  filter(attached == TRUE) %>%
  dplyr::select(loadedversion, date) %>%
  rownames_to_column()

colnames(df_session_packages) <- c("Package", "Loaded Version", "Date")

kable(
  df_session_packages,
  booktabs = TRUE,
  caption = "Packages required for data management and analysis."
) %>%
  kable_styling(
    full_width = FALSE,
    latex_options = c("HOLD_position", "striped")
  )
```
