---
title: "TRhizo-urbanMicrobiome"
subtitle: "Effect Size Calculations"
author: "David Murray-Stoker"
output:
  pdf_document:
    toc: true
    toc_depth: 5
    fig_caption: yes
    latex_engine: xelatex
always_allow_html: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(results = "hold", fig.pos = "H", fig.align = "center", out.width = "92.5%")
options(knitr.graphics.error = FALSE)
kableExtra::usepackage_latex("float")
```

```{r Load Packages for R Markdown, include = FALSE}
library(kableExtra)
library(knitr)
```





\newpage
# Load Packages & Data

\vspace{10pt}

```{r Load Packages, include = FALSE}
## Load the tidyverse
library(tidyverse)

## Packages for analyses
library(easystats)
library(mgcv)

## Load the workspaces
# Diversity and composition analyses
load("data_analysis/7-diversity_composition_analyses/diversity_composition-workspace.RData")
# Mutualistic bacteria analyses
load("data_analysis/10-bacterial_functional_groups/mutualistic_bacteria-workspace.RData")
# Pathogenic bacteria analyses
load("data_analysis/10-bacterial_functional_groups/pathogenic_bacteria-workspace.RData")
# Ecosystem function bacteria analyses
load("data_analysis/10-bacterial_functional_groups/ecosystem_function_bacteria-workspace.RData")
# Carbon and nitrogen analyses
load("data_analysis/6-carbon_nitrogen_analyses/carbon_nitrogen-workspace.RData")
```





\newpage
# Alpha Diversity Effect Sizes

## ASV Richness

### Distance

```{r Effect Size Calculations: ASV Richness by Distance, echo = TRUE}
## Get model residuals
ASV.richness.by.distance.residual.df <- df.residual(
  ASV.richness.by.distance.GAMM
)

## Calculate effect sizes
# Compartment (parametric)
ASV.richness.by.distance.compartment.eta.squared <- F_to_eta2(
  652.9, 1, ASV.richness.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
ASV.richness.by.distance.root.eta.squared <- F_to_eta2(
  0.087, 0.411, ASV.richness.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
ASV.richness.by.distance.soil.eta.squared <- F_to_eta2(
  2.848, 2.939, ASV.richness.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of population random effect
ASV.richness.by.distance.population.eta.squared <- F_to_eta2(
  0.292, 7.687, ASV.richness.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
ASV.richness.by.distance.effect.sizes <- tibble(
  Compartment = ASV.richness.by.distance.compartment.eta.squared,
  Smooth_by_Root = ASV.richness.by.distance.root.eta.squared,
  Smooth_by_Soil = ASV.richness.by.distance.soil.eta.squared,
  Population = ASV.richness.by.distance.population.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: ASV Richness by HII, echo = TRUE}
## Get model residuals
ASV.richness.by.HII.residual.df <- df.residual(
  ASV.richness.by.HII.GAMM
)

## Calculate effect sizes
# Compartment (parametric)
ASV.richness.by.HII.compartment.eta.squared <- F_to_eta2(
  637.2, 1, ASV.richness.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
ASV.richness.by.HII.root.HII.eta.squared <- F_to_eta2(
  0.138, 0.505, ASV.richness.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
ASV.richness.by.HII.soil.HII.eta.squared <- F_to_eta2(
  1.336, 0.896, ASV.richness.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of population random effect
ASV.richness.by.HII.population.eta.squared <- F_to_eta2(
  0.411, 9.908, ASV.richness.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
ASV.richness.by.ISC.effect.sizes <- tibble(
  Compartment = ASV.richness.by.HII.compartment.eta.squared,
  Smooth_by_Root = ASV.richness.by.HII.root.HII.eta.squared,
  Smooth_by_Soil = ASV.richness.by.HII.soil.HII.eta.squared,
  Population = ASV.richness.by.HII.population.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: ASV Richness by ISC, echo = TRUE}
## Get model residuals
ASV.richness.by.ISC.residual.df <- df.residual(
  ASV.richness.by.ISC.GAMM
)

## Calculate effect sizes
# Compartment (parametric)
ASV.richness.by.ISC.compartment.eta.squared <- F_to_eta2(
  665.2, 1, ASV.richness.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
ASV.richness.by.ISC.root.ISC.eta.squared <- F_to_eta2(
  0.135, 0.551, ASV.richness.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
ASV.richness.by.ISC.soil.ISC.eta.squared <- F_to_eta2(
  4.582, 5.933, ASV.richness.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of population random effect
ASV.richness.by.ISC.population.eta.squared <- F_to_eta2(
  0.003, 0.092, ASV.richness.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
ASV.richness.by.HII.effect.sizes <- tibble(
  Compartment = ASV.richness.by.ISC.compartment.eta.squared,
  Smooth_by_Root = ASV.richness.by.ISC.root.ISC.eta.squared,
  Smooth_by_Soil = ASV.richness.by.ISC.soil.ISC.eta.squared,
  Population = ASV.richness.by.ISC.population.eta.squared
)
```



\newpage
### ASV Richness Effect Size Summary

```{r ASV Richness Effect Size Summary Table, echo = FALSE}
ASV.richness.effect.sizes <- bind_rows(
  ASV.richness.by.distance.effect.sizes,
  ASV.richness.by.HII.effect.sizes,
  ASV.richness.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Population)

kable(
  ASV.richness.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the ASV richness GAMMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Inverse Simpson

### Distance

```{r Effect Size Calculations: Inverse Simpson by Distance, echo = TRUE}
## Get model residuals
inverse.simpson.by.distance.residual.df <- df.residual(
  inverse.simpson.by.distance.GAMM
)

## Calculate effect sizes
# Compartment (parametric)
inverse.simpson.by.distance.compartment.eta.squared <- F_to_eta2(
  1331, 1, inverse.simpson.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
inverse.simpson.by.distance.root.eta.squared <- F_to_eta2(
  0.0001, 0.002, inverse.simpson.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
inverse.simpson.by.distance.soil.eta.squared <- F_to_eta2(
  10.988, 4.038, inverse.simpson.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of population random effect
inverse.simpson.by.distance.population.eta.squared <- F_to_eta2(
  3.694, 26.605, inverse.simpson.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
inverse.simpson.by.distance.effect.sizes <- tibble(
  Compartment = inverse.simpson.by.distance.compartment.eta.squared,
  Smooth_by_Root = inverse.simpson.by.distance.root.eta.squared,
  Smooth_by_Soil = inverse.simpson.by.distance.soil.eta.squared,
  Population = inverse.simpson.by.distance.population.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Inverse Simpson by HII, echo = TRUE}
## Get model residuals
inverse.simpson.by.HII.residual.df <- df.residual(
  inverse.simpson.by.HII.GAMM
)

## Calculate effect sizes
# Compartment (parametric)
inverse.simpson.by.HII.compartment.eta.squared <- F_to_eta2(
  1347, 1, inverse.simpson.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
inverse.simpson.by.HII.root.HII.eta.squared <- F_to_eta2(
  0.00001, 0.001, inverse.simpson.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
inverse.simpson.by.HII.soil.HII.eta.squared <- F_to_eta2(
  14.595, 4.233, inverse.simpson.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of population random effect
inverse.simpson.by.HII.population.eta.squared <- F_to_eta2(
  2.925, 25.114, inverse.simpson.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
inverse.simpson.by.ISC.effect.sizes <- tibble(
  Compartment = inverse.simpson.by.HII.compartment.eta.squared,
  Smooth_by_Root = inverse.simpson.by.HII.root.HII.eta.squared,
  Smooth_by_Soil = inverse.simpson.by.HII.soil.HII.eta.squared,
  Population = inverse.simpson.by.HII.population.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Inverse Simpson by ISC, echo = TRUE}
## Get model residuals
inverse.simpson.by.ISC.residual.df <- df.residual(
  inverse.simpson.by.ISC.GAMM
)

## Calculate effect sizes
# Compartment (parametric)
inverse.simpson.by.ISC.compartment.eta.squared <- F_to_eta2(
  1324, 1, inverse.simpson.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
inverse.simpson.by.ISC.root.ISC.eta.squared <- F_to_eta2(
  0.00001, 0.002, inverse.simpson.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
inverse.simpson.by.ISC.soil.ISC.eta.squared <- F_to_eta2(
  10.431, 4.372, inverse.simpson.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of population random effect
inverse.simpson.by.ISC.population.eta.squared <- F_to_eta2(
  3.523, 26.064, inverse.simpson.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
inverse.simpson.by.HII.effect.sizes <- tibble(
  Compartment = inverse.simpson.by.ISC.compartment.eta.squared,
  Smooth_by_Root = inverse.simpson.by.ISC.root.ISC.eta.squared,
  Smooth_by_Soil = inverse.simpson.by.ISC.soil.ISC.eta.squared,
  Population = inverse.simpson.by.ISC.population.eta.squared
)
```



\newpage
### Inverse Simpson Effect Size Summary

```{r Inverse Simpson Effect Size Summary Table, echo = FALSE}
inverse.simpson.effect.sizes <- bind_rows(
  inverse.simpson.by.distance.effect.sizes,
  inverse.simpson.by.HII.effect.sizes,
  inverse.simpson.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Population)

kable(
  inverse.simpson.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the inverse Simpson GAMMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## ASV Evenness

### Distance

```{r Effect Size Calculations: ASV Evenness by Distance, echo = TRUE}
## Get model residuals
ASV.evenness.by.distance.residual.df <- df.residual(
  ASV.evenness.by.distance.GAMM
)

## Calculate effect sizes
# Compartment (parametric)
ASV.evenness.by.distance.compartment.eta.squared <- F_to_eta2(
  476.1, 1, ASV.evenness.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
ASV.evenness.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, ASV.evenness.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
ASV.evenness.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, ASV.evenness.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of population random effect
ASV.evenness.by.distance.population.eta.squared <- F_to_eta2(
  2.787, 25.038, ASV.evenness.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
ASV.evenness.by.distance.effect.sizes <- tibble(
  Compartment = ASV.evenness.by.distance.compartment.eta.squared,
  Smooth_by_Root = ASV.evenness.by.distance.root.eta.squared,
  Smooth_by_Soil = ASV.evenness.by.distance.soil.eta.squared,
  Population = ASV.evenness.by.distance.population.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: ASV Evenness by HII, echo = TRUE}
## Get model residuals
ASV.evenness.by.HII.residual.df <- df.residual(
  ASV.evenness.by.HII.GAMM
)

## Calculate effect sizes
# Compartment (parametric)
ASV.evenness.by.HII.compartment.eta.squared <- F_to_eta2(
  637.2, 1, ASV.evenness.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
ASV.evenness.by.HII.root.HII.eta.squared <- F_to_eta2(
  0.006, 0.043, ASV.evenness.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
ASV.evenness.by.HII.soil.HII.eta.squared <- F_to_eta2(
  0.00001, 0.001, ASV.evenness.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of population random effect
ASV.evenness.by.HII.population.eta.squared <- F_to_eta2(
  2.786, 25.031, ASV.evenness.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
ASV.evenness.by.ISC.effect.sizes <- tibble(
  Compartment = ASV.evenness.by.HII.compartment.eta.squared,
  Smooth_by_Root = ASV.evenness.by.HII.root.HII.eta.squared,
  Smooth_by_Soil = ASV.evenness.by.HII.soil.HII.eta.squared,
  Population = ASV.evenness.by.HII.population.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: ASV Evenness by ISC, echo = TRUE}
## Get model residuals
ASV.evenness.by.ISC.residual.df <- df.residual(
  ASV.evenness.by.ISC.GAMM
)

## Calculate effect sizes
# Compartment (parametric)
ASV.evenness.by.ISC.compartment.eta.squared <- F_to_eta2(
  476.5, 1, ASV.evenness.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
ASV.evenness.by.ISC.root.ISC.eta.squared <- F_to_eta2(
  0.00001, 0.00001, ASV.evenness.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
ASV.evenness.by.ISC.soil.ISC.eta.squared <- F_to_eta2(
  0.173, 0.414, ASV.evenness.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of population random effect
ASV.evenness.by.ISC.population.eta.squared <- F_to_eta2(
  2.737, 24.884, ASV.evenness.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
ASV.evenness.by.HII.effect.sizes <- tibble(
  Compartment = ASV.evenness.by.ISC.compartment.eta.squared,
  Smooth_by_Root = ASV.evenness.by.ISC.root.ISC.eta.squared,
  Smooth_by_Soil = ASV.evenness.by.ISC.soil.ISC.eta.squared,
  Population = ASV.evenness.by.ISC.population.eta.squared
)
```



\newpage
### ASV Evenness Effect Size Summary

```{r ASV Evenness Effect Size Summary Table, echo = FALSE}
ASV.evenness.effect.sizes <- bind_rows(
  ASV.evenness.by.distance.effect.sizes,
  ASV.evenness.by.HII.effect.sizes,
  ASV.evenness.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Population)

kable(
  ASV.evenness.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the ASV evenness GAMMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Faith's PD

### Distance

```{r Effect Size Calculations: Faiths PD by Distance, echo = TRUE}
## Get model residuals
faiths.PD.by.distance.residual.df <- df.residual(
  faiths.PD.by.distance.GAMM
)

## Calculate effect sizes
# Compartment (parametric)
faiths.PD.by.distance.compartment.eta.squared <- F_to_eta2(
  809.2, 1, faiths.PD.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
faiths.PD.by.distance.root.eta.squared <- F_to_eta2(
  0.151, 0.533, faiths.PD.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
faiths.PD.by.distance.soil.eta.squared <- F_to_eta2(
  4.837, 3.636, faiths.PD.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of population random effect
faiths.PD.by.distance.population.eta.squared <- F_to_eta2(
  0.374, 9.280, faiths.PD.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
faiths.PD.by.distance.effect.sizes <- tibble(
  Compartment = faiths.PD.by.distance.compartment.eta.squared,
  Smooth_by_Root = faiths.PD.by.distance.root.eta.squared,
  Smooth_by_Soil = faiths.PD.by.distance.soil.eta.squared,
  Population = faiths.PD.by.distance.population.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Faiths PD by HII, echo = TRUE}
## Get model residuals
faiths.PD.by.HII.residual.df <- df.residual(
  faiths.PD.by.HII.GAMM
)

## Calculate effect sizes
# Compartment (parametric)
faiths.PD.by.HII.compartment.eta.squared <- F_to_eta2(
  809.2, 1, faiths.PD.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
faiths.PD.by.HII.root.HII.eta.squared <- F_to_eta2(
  0.332, 0.678, faiths.PD.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
faiths.PD.by.HII.soil.HII.eta.squared <- F_to_eta2(
  2.258, 0.927, faiths.PD.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of population random effect
faiths.PD.by.HII.population.eta.squared <- F_to_eta2(
  0.593, 12.636, faiths.PD.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
faiths.PD.by.ISC.effect.sizes <- tibble(
  Compartment = faiths.PD.by.HII.compartment.eta.squared,
  Smooth_by_Root = faiths.PD.by.HII.root.HII.eta.squared,
  Smooth_by_Soil = faiths.PD.by.HII.soil.HII.eta.squared,
  Population = faiths.PD.by.HII.population.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Faiths PD by ISC, echo = TRUE}
## Get model residuals
faiths.PD.by.ISC.residual.df <- df.residual(
  faiths.PD.by.ISC.GAMM
)

## Calculate effect sizes
# Compartment (parametric)
faiths.PD.by.ISC.compartment.eta.squared <- F_to_eta2(
  856.4, 1, faiths.PD.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
faiths.PD.by.ISC.root.ISC.eta.squared <- F_to_eta2(
  0.230, 0.678, faiths.PD.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
faiths.PD.by.ISC.soil.ISC.eta.squared <- F_to_eta2(
  6.677, 6.443, faiths.PD.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of population random effect
faiths.PD.by.ISC.population.eta.squared <- F_to_eta2(
  0.035, 1.149, faiths.PD.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
faiths.PD.by.HII.effect.sizes <- tibble(
  Compartment = faiths.PD.by.ISC.compartment.eta.squared,
  Smooth_by_Root = faiths.PD.by.ISC.root.ISC.eta.squared,
  Smooth_by_Soil = faiths.PD.by.ISC.soil.ISC.eta.squared,
  Population = faiths.PD.by.ISC.population.eta.squared
)
```



\newpage
### Faiths PD Effect Size Summary

```{r Faiths PD Effect Size Summary Table, echo = FALSE}
faiths.PD.effect.sizes <- bind_rows(
  faiths.PD.by.distance.effect.sizes,
  faiths.PD.by.HII.effect.sizes,
  faiths.PD.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Population)

kable(
  faiths.PD.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the ASV richness GAMMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```










\newpage
# Beta Diversity Effect Sizes

## Bray-Curtis Distance

### Distance

```{r Effect Size Calculations: BC Dispersion by Distance, echo = TRUE}
## Get model residuals
BC.multivariate.dispersion.by.distance.residual.df <- df.residual(
  BC.multivariate.dispersion.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
BC.dispersion.by.distance.compartment.eta.squared <- F_to_eta2(
  109.6, 1, BC.multivariate.dispersion.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
BC.dispersion.by.distance.root.eta.squared <- F_to_eta2(
  1.002, 2.226, BC.multivariate.dispersion.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
BC.dispersion.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, BC.multivariate.dispersion.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
BC.dispersion.by.distance.effect.sizes <- tibble(
  Compartment = BC.dispersion.by.distance.compartment.eta.squared,
  Smooth_by_Root = BC.dispersion.by.distance.root.eta.squared,
  Smooth_by_Soil = BC.dispersion.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: BC Dispersion by HII, echo = TRUE}
## Get model residuals
BC.multivariate.dispersion.by.HII.residual.df <- df.residual(
  BC.multivariate.dispersion.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
BC.dispersion.by.HII.compartment.eta.squared <- F_to_eta2(
  96.9, 1, BC.multivariate.dispersion.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
BC.dispersion.by.HII.root.eta.squared <- F_to_eta2(
  0.016, 0.127, BC.multivariate.dispersion.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
BC.dispersion.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, BC.multivariate.dispersion.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
BC.dispersion.by.HII.effect.sizes <- tibble(
  Compartment = BC.dispersion.by.HII.compartment.eta.squared,
  Smooth_by_Root = BC.dispersion.by.HII.root.eta.squared,
  Smooth_by_Soil = BC.dispersion.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: BC Dispersion by ISC, echo = TRUE}
## Get model residuals
BC.multivariate.dispersion.by.ISC.residual.df <- df.residual(
  BC.multivariate.dispersion.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
BC.dispersion.by.ISC.compartment.eta.squared <- F_to_eta2(
  96.7, 1, BC.multivariate.dispersion.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
BC.dispersion.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, BC.multivariate.dispersion.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
BC.dispersion.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, BC.multivariate.dispersion.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
BC.dispersion.by.ISC.effect.sizes <- tibble(
  Compartment = BC.dispersion.by.ISC.compartment.eta.squared,
  Smooth_by_Root = BC.dispersion.by.ISC.root.eta.squared,
  Smooth_by_Soil = BC.dispersion.by.ISC.soil.eta.squared
)
```



\newpage
### Bray-Curtis Multivariate Dispersion Effect Size Summary

```{r BC Dispersion Effect Size Summary Table, echo = FALSE}
BC.dispersion.effect.sizes <- bind_rows(
  BC.dispersion.by.distance.effect.sizes,
  BC.dispersion.by.HII.effect.sizes,
  BC.dispersion.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  BC.dispersion.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Bray-Curtis multivariate dispersion GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## UniFrac Distance

### Distance

```{r Effect Size Calculations: UniFrac Dispersion by Distance, echo = TRUE}
## Get model residuals
UniFrac.multivariate.dispersion.by.distance.residual.df <- df.residual(
  UniFrac.multivariate.dispersion.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
UniFrac.dispersion.by.distance.compartment.eta.squared <- F_to_eta2(
  68.4, 1, UniFrac.multivariate.dispersion.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
UniFrac.dispersion.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, UniFrac.multivariate.dispersion.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
UniFrac.dispersion.by.distance.soil.eta.squared <- F_to_eta2(
  0.001, 0.012, UniFrac.multivariate.dispersion.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
UniFrac.dispersion.by.distance.effect.sizes <- tibble(
  Compartment = UniFrac.dispersion.by.distance.compartment.eta.squared,
  Smooth_by_Root = UniFrac.dispersion.by.distance.root.eta.squared,
  Smooth_by_Soil = UniFrac.dispersion.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: UniFrac Dispersion by HII, echo = TRUE}
## Get model residuals
UniFrac.multivariate.dispersion.by.HII.residual.df <- df.residual(
  UniFrac.multivariate.dispersion.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
UniFrac.dispersion.by.HII.compartment.eta.squared <- F_to_eta2(
  71.7, 1, UniFrac.multivariate.dispersion.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
UniFrac.dispersion.by.HII.root.eta.squared <- F_to_eta2(
  0.007, 0.063, UniFrac.multivariate.dispersion.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
UniFrac.dispersion.by.HII.soil.eta.squared <- F_to_eta2(
  0.357, 0.763, UniFrac.multivariate.dispersion.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
UniFrac.dispersion.by.HII.effect.sizes <- tibble(
  Compartment = UniFrac.dispersion.by.HII.compartment.eta.squared,
  Smooth_by_Root = UniFrac.dispersion.by.HII.root.eta.squared,
  Smooth_by_Soil = UniFrac.dispersion.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: UniFrac Dispersion by ISC, echo = TRUE}
## Get model residuals
UniFrac.multivariate.dispersion.by.ISC.residual.df <- df.residual(
  UniFrac.multivariate.dispersion.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
UniFrac.dispersion.by.ISC.compartment.eta.squared <- F_to_eta2(
  68.4, 1, UniFrac.multivariate.dispersion.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
UniFrac.dispersion.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, UniFrac.multivariate.dispersion.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
UniFrac.dispersion.by.ISC.soil.eta.squared <- F_to_eta2(
  0.933, 2.124, UniFrac.multivariate.dispersion.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
UniFrac.dispersion.by.ISC.effect.sizes <- tibble(
  Compartment = UniFrac.dispersion.by.ISC.compartment.eta.squared,
  Smooth_by_Root = UniFrac.dispersion.by.ISC.root.eta.squared,
  Smooth_by_Soil = UniFrac.dispersion.by.ISC.soil.eta.squared
)
```



\newpage
### UniFrac Multivariate Dispersion Effect Size Summary

```{r UniFrac Dispersion Effect Size Summary Table, echo = FALSE}
UniFrac.dispersion.effect.sizes <- bind_rows(
  UniFrac.dispersion.by.distance.effect.sizes,
  UniFrac.dispersion.by.HII.effect.sizes,
  UniFrac.dispersion.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  UniFrac.dispersion.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the UniFrac multivariate dispersion GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Weighted UniFrac Distance

### Distance

```{r Effect Size Calculations: Weighted UniFrac Dispersion by Distance, echo = TRUE}
## Get model residuals
weighted.UniFrac.multivariate.dispersion.by.distance.residual.df <- df.residual(
  weighted.UniFrac.multivariate.dispersion.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
weighted.UniFrac.dispersion.by.distance.compartment.eta.squared <- F_to_eta2(
  122.4, 1, weighted.UniFrac.multivariate.dispersion.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
weighted.UniFrac.dispersion.by.distance.root.eta.squared <- F_to_eta2(
  1.122, 2.255, weighted.UniFrac.multivariate.dispersion.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
weighted.UniFrac.dispersion.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, weighted.UniFrac.multivariate.dispersion.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
weighted.UniFrac.dispersion.by.distance.effect.sizes <- tibble(
  Compartment = weighted.UniFrac.dispersion.by.distance.compartment.eta.squared,
  Smooth_by_Root = weighted.UniFrac.dispersion.by.distance.root.eta.squared,
  Smooth_by_Soil = weighted.UniFrac.dispersion.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Weighted UniFrac Dispersion by HII, echo = TRUE}
## Get model residuals
weighted.UniFrac.multivariate.dispersion.by.HII.residual.df <- df.residual(
  weighted.UniFrac.multivariate.dispersion.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
weighted.UniFrac.dispersion.by.HII.compartment.eta.squared <- F_to_eta2(
  106.6, 1, weighted.UniFrac.multivariate.dispersion.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
weighted.UniFrac.dispersion.by.HII.root.eta.squared <- F_to_eta2(
  0.001, 0.00001, weighted.UniFrac.multivariate.dispersion.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
weighted.UniFrac.dispersion.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, weighted.UniFrac.multivariate.dispersion.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
weighted.UniFrac.dispersion.by.HII.effect.sizes <- tibble(
  Compartment = weighted.UniFrac.dispersion.by.HII.compartment.eta.squared,
  Smooth_by_Root = weighted.UniFrac.dispersion.by.HII.root.eta.squared,
  Smooth_by_Soil = weighted.UniFrac.dispersion.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Weighted UniFrac Dispersion by ISC, echo = TRUE}
## Get model residuals
weighted.UniFrac.multivariate.dispersion.by.ISC.residual.df <- df.residual(
  weighted.UniFrac.multivariate.dispersion.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
weighted.UniFrac.dispersion.by.ISC.compartment.eta.squared <- F_to_eta2(
  106.6, 1, weighted.UniFrac.multivariate.dispersion.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
weighted.UniFrac.dispersion.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, weighted.UniFrac.multivariate.dispersion.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
weighted.UniFrac.dispersion.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, weighted.UniFrac.multivariate.dispersion.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
weighted.UniFrac.dispersion.by.ISC.effect.sizes <- tibble(
  Compartment = weighted.UniFrac.dispersion.by.ISC.compartment.eta.squared,
  Smooth_by_Root = weighted.UniFrac.dispersion.by.ISC.root.eta.squared,
  Smooth_by_Soil = weighted.UniFrac.dispersion.by.ISC.soil.eta.squared
)
```



\newpage
### Weighted UniFrac Multivariate Dispersion Effect Size Summary

```{r Weighted UniFrac Dispersion Effect Size Summary Table, echo = FALSE}
weighted.UniFrac.dispersion.effect.sizes <- bind_rows(
  weighted.UniFrac.dispersion.by.distance.effect.sizes,
  weighted.UniFrac.dispersion.by.HII.effect.sizes,
  weighted.UniFrac.dispersion.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  weighted.UniFrac.dispersion.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the weighted UniFrac multivariate dispersion GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```







\newpage
# Mutualistic Bacteria

## Allorhizobium

### Distance

```{r Effect Size Calculations: Allorhizobium by Distance, echo = TRUE}
## Get model residuals
allorhizobium.by.distance.residual.df <- df.residual(
  allorhizobium.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
allorhizobium.by.distance.compartment.eta.squared <- F_to_eta2(
  12.7, 1, allorhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
allorhizobium.by.distance.root.eta.squared <- F_to_eta2(
  2.535, 2.644, allorhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
allorhizobium.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, allorhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
allorhizobium.by.distance.effect.sizes <- tibble(
  Compartment = allorhizobium.by.distance.compartment.eta.squared,
  Smooth_by_Root = allorhizobium.by.distance.root.eta.squared,
  Smooth_by_Soil = allorhizobium.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Allorhizobium by HII, echo = TRUE}
## Get model residuals
allorhizobium.by.HII.residual.df <- df.residual(
  allorhizobium.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
allorhizobium.by.HII.compartment.eta.squared <- F_to_eta2(
  10.8, 1, allorhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
allorhizobium.by.HII.root.eta.squared <- F_to_eta2(
  1.051, 0.905, allorhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
allorhizobium.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, allorhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
allorhizobium.by.HII.effect.sizes <- tibble(
  Compartment = allorhizobium.by.HII.compartment.eta.squared,
  Smooth_by_Root = allorhizobium.by.HII.root.eta.squared,
  Smooth_by_Soil = allorhizobium.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Allorhizobium by ISC, echo = TRUE}
## Get model residuals
allorhizobium.by.ISC.residual.df <- df.residual(
  allorhizobium.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
allorhizobium.by.ISC.compartment.eta.squared <- F_to_eta2(
  9.781, 1, allorhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
allorhizobium.by.ISC.root.eta.squared <- F_to_eta2(
  0.215, 0.671, allorhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
allorhizobium.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, allorhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
allorhizobium.by.ISC.effect.sizes <- tibble(
  Compartment = allorhizobium.by.ISC.compartment.eta.squared,
  Smooth_by_Root = allorhizobium.by.ISC.root.eta.squared,
  Smooth_by_Soil = allorhizobium.by.ISC.soil.eta.squared
)
```



\newpage
### Allorhizobium Effect Size Summary

```{r Allorhizobium Effect Size Summary Table, echo = FALSE}
allorhizobium.effect.sizes <- bind_rows(
  allorhizobium.by.distance.effect.sizes,
  allorhizobium.by.HII.effect.sizes,
  allorhizobium.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  allorhizobium.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Allorhizobium abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Bradyrhizobium

### Distance

```{r Effect Size Calculations: Bradyrhizobium by Distance, echo = TRUE}
## Get model residuals
bradyrhizobium.by.distance.residual.df <- df.residual(
  bradyrhizobium.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
bradyrhizobium.by.distance.compartment.eta.squared <- F_to_eta2(
  36.4, 1, bradyrhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
bradyrhizobium.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, bradyrhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
bradyrhizobium.by.distance.soil.eta.squared <- F_to_eta2(
  0.589, 1.894, bradyrhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
bradyrhizobium.by.distance.effect.sizes <- tibble(
  Compartment = bradyrhizobium.by.distance.compartment.eta.squared,
  Smooth_by_Root = bradyrhizobium.by.distance.root.eta.squared,
  Smooth_by_Soil = bradyrhizobium.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Bradyrhizobium by HII, echo = TRUE}
## Get model residuals
bradyrhizobium.by.HII.residual.df <- df.residual(
  bradyrhizobium.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
bradyrhizobium.by.HII.compartment.eta.squared <- F_to_eta2(
  33.8, 1, bradyrhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
bradyrhizobium.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, bradyrhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
bradyrhizobium.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, bradyrhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
bradyrhizobium.by.HII.effect.sizes <- tibble(
  Compartment = bradyrhizobium.by.HII.compartment.eta.squared,
  Smooth_by_Root = bradyrhizobium.by.HII.root.eta.squared,
  Smooth_by_Soil = bradyrhizobium.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Bradyrhizobium by ISC, echo = TRUE}
## Get model residuals
bradyrhizobium.by.ISC.residual.df <- df.residual(
  bradyrhizobium.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
bradyrhizobium.by.ISC.compartment.eta.squared <- F_to_eta2(
  36.6, 1, bradyrhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
bradyrhizobium.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, bradyrhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
bradyrhizobium.by.ISC.soil.eta.squared <- F_to_eta2(
  0.634, 1.948, bradyrhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
bradyrhizobium.by.ISC.effect.sizes <- tibble(
  Compartment = bradyrhizobium.by.ISC.compartment.eta.squared,
  Smooth_by_Root = bradyrhizobium.by.ISC.root.eta.squared,
  Smooth_by_Soil = bradyrhizobium.by.ISC.soil.eta.squared
)
```



\newpage
### Bradyrhizobium Effect Size Summary

```{r Bradyrhizobium Effect Size Summary Table, echo = FALSE}
bradyrhizobium.effect.sizes <- bind_rows(
  bradyrhizobium.by.distance.effect.sizes,
  bradyrhizobium.by.HII.effect.sizes,
  bradyrhizobium.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  bradyrhizobium.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Bradyrhizobium abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Mesorhizobium

### Distance

```{r Effect Size Calculations: Mesorhizobium by Distance, echo = TRUE}
## Get model residuals
mesorhizobium.by.distance.residual.df <- df.residual(
  mesorhizobium.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
mesorhizobium.by.distance.compartment.eta.squared <- F_to_eta2(
  33.1, 1, mesorhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
mesorhizobium.by.distance.root.eta.squared <- F_to_eta2(
  0.043, 0.278, mesorhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
mesorhizobium.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, mesorhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
mesorhizobium.by.distance.effect.sizes <- tibble(
  Compartment = mesorhizobium.by.distance.compartment.eta.squared,
  Smooth_by_Root = mesorhizobium.by.distance.root.eta.squared,
  Smooth_by_Soil = mesorhizobium.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Mesorhizobium by HII, echo = TRUE}
## Get model residuals
mesorhizobium.by.HII.residual.df <- df.residual(
  mesorhizobium.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
mesorhizobium.by.HII.compartment.eta.squared <- F_to_eta2(
  37.0, 1, mesorhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
mesorhizobium.by.HII.root.eta.squared <- F_to_eta2(
  0.005, 0.046, mesorhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
mesorhizobium.by.HII.soil.eta.squared <- F_to_eta2(
  0.936, 2.229, mesorhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
mesorhizobium.by.HII.effect.sizes <- tibble(
  Compartment = mesorhizobium.by.HII.compartment.eta.squared,
  Smooth_by_Root = mesorhizobium.by.HII.root.eta.squared,
  Smooth_by_Soil = mesorhizobium.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Mesorhizobium by ISC, echo = TRUE}
## Get model residuals
mesorhizobium.by.ISC.residual.df <- df.residual(
  mesorhizobium.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
mesorhizobium.by.ISC.compartment.eta.squared <- F_to_eta2(
  33.4, 1, mesorhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
mesorhizobium.by.ISC.root.eta.squared <- F_to_eta2(
  0.11, 0.5, mesorhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
mesorhizobium.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, mesorhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
mesorhizobium.by.ISC.effect.sizes <- tibble(
  Compartment = mesorhizobium.by.ISC.compartment.eta.squared,
  Smooth_by_Root = mesorhizobium.by.ISC.root.eta.squared,
  Smooth_by_Soil = mesorhizobium.by.ISC.soil.eta.squared
)
```



\newpage
### Mesorhizobium Effect Size Summary

```{r Mesorhizobium Effect Size Summary Table, echo = FALSE}
mesorhizobium.effect.sizes <- bind_rows(
  mesorhizobium.by.distance.effect.sizes,
  mesorhizobium.by.HII.effect.sizes,
  mesorhizobium.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  mesorhizobium.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Mesorhizobium abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Pararhizobium

### Distance

```{r Effect Size Calculations: Pararhizobium by Distance, echo = TRUE}
## Get model residuals
pararhizobium.by.distance.residual.df <- df.residual(
  pararhizobium.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
pararhizobium.by.distance.compartment.eta.squared <- F_to_eta2(
  142.8, 1, pararhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
pararhizobium.by.distance.root.eta.squared <- F_to_eta2(
  0.172, 0.612, pararhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
pararhizobium.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, pararhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
pararhizobium.by.distance.effect.sizes <- tibble(
  Compartment = pararhizobium.by.distance.compartment.eta.squared,
  Smooth_by_Root = pararhizobium.by.distance.root.eta.squared,
  Smooth_by_Soil = pararhizobium.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Pararhizobium by HII, echo = TRUE}
## Get model residuals
pararhizobium.by.HII.residual.df <- df.residual(
  pararhizobium.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
pararhizobium.by.HII.compartment.eta.squared <- F_to_eta2(
  141.2, 1, pararhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
pararhizobium.by.HII.root.eta.squared <- F_to_eta2(
  0.082, 0.424, pararhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
pararhizobium.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, pararhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
pararhizobium.by.HII.effect.sizes <- tibble(
  Compartment = pararhizobium.by.HII.compartment.eta.squared,
  Smooth_by_Root = pararhizobium.by.HII.root.eta.squared,
  Smooth_by_Soil = pararhizobium.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Pararhizobium by ISC, echo = TRUE}
## Get model residuals
pararhizobium.by.ISC.residual.df <- df.residual(
  pararhizobium.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
pararhizobium.by.ISC.compartment.eta.squared <- F_to_eta2(
  140.8, 1, pararhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
pararhizobium.by.ISC.root.eta.squared <- F_to_eta2(
  0.061, 0.357, pararhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
pararhizobium.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, pararhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
pararhizobium.by.ISC.effect.sizes <- tibble(
  Compartment = pararhizobium.by.ISC.compartment.eta.squared,
  Smooth_by_Root = pararhizobium.by.ISC.root.eta.squared,
  Smooth_by_Soil = pararhizobium.by.ISC.soil.eta.squared
)
```



\newpage
### Pararhizobium Effect Size Summary

```{r Pararhizobium Effect Size Summary Table, echo = FALSE}
pararhizobium.effect.sizes <- bind_rows(
  pararhizobium.by.distance.effect.sizes,
  pararhizobium.by.HII.effect.sizes,
  pararhizobium.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  pararhizobium.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Pararhizobium abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```




\newpage
## Rhizobium

### Distance

```{r Effect Size Calculations: Rhizobium by Distance, echo = TRUE}
## Get model residuals
rhizobium.by.distance.residual.df <- df.residual(
  rhizobium.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
rhizobium.by.distance.compartment.eta.squared <- F_to_eta2(
  109.3, 1, rhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
rhizobium.by.distance.root.eta.squared <- F_to_eta2(
  1.956, 3.196, rhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
rhizobium.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, rhizobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
rhizobium.by.distance.effect.sizes <- tibble(
  Compartment = rhizobium.by.distance.compartment.eta.squared,
  Smooth_by_Root = rhizobium.by.distance.root.eta.squared,
  Smooth_by_Soil = rhizobium.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Rhizobium by HII, echo = TRUE}
## Get model residuals
rhizobium.by.HII.residual.df <- df.residual(
  rhizobium.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
rhizobium.by.HII.compartment.eta.squared <- F_to_eta2(
  88.7, 1, rhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
rhizobium.by.HII.root.eta.squared <- F_to_eta2(
  0.165, 0.598, rhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
rhizobium.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, rhizobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
rhizobium.by.HII.effect.sizes <- tibble(
  Compartment = rhizobium.by.HII.compartment.eta.squared,
  Smooth_by_Root = rhizobium.by.HII.root.eta.squared,
  Smooth_by_Soil = rhizobium.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Rhizobium by ISC, echo = TRUE}
## Get model residuals
rhizobium.by.ISC.residual.df <- df.residual(
  rhizobium.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
rhizobium.by.ISC.compartment.eta.squared <- F_to_eta2(
  145.6, 1, rhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
rhizobium.by.ISC.root.eta.squared <- F_to_eta2(
  5.115, 5.959, rhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
rhizobium.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, rhizobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
rhizobium.by.ISC.effect.sizes <- tibble(
  Compartment = rhizobium.by.ISC.compartment.eta.squared,
  Smooth_by_Root = rhizobium.by.ISC.root.eta.squared,
  Smooth_by_Soil = rhizobium.by.ISC.soil.eta.squared
)
```



\newpage
### Rhizobium Effect Size Summary

```{r Rhizobium Effect Size Summary Table, echo = FALSE}
rhizobium.effect.sizes <- bind_rows(
  rhizobium.by.distance.effect.sizes,
  rhizobium.by.HII.effect.sizes,
  rhizobium.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  rhizobium.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Rhizobium abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Shinella

### Distance

```{r Effect Size Calculations: Shinella by Distance, echo = TRUE}
## Get model residuals
shinella.by.distance.residual.df <- df.residual(
  shinella.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
shinella.by.distance.compartment.eta.squared <- F_to_eta2(
  40.2, 1, shinella.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
shinella.by.distance.root.eta.squared <- F_to_eta2(
  0.579, 0.869, shinella.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
shinella.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, shinella.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
shinella.by.distance.effect.sizes <- tibble(
  Compartment = shinella.by.distance.compartment.eta.squared,
  Smooth_by_Root = shinella.by.distance.root.eta.squared,
  Smooth_by_Soil = shinella.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Shinella by HII, echo = TRUE}
## Get model residuals
shinella.by.HII.residual.df <- df.residual(
  shinella.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
shinella.by.HII.compartment.eta.squared <- F_to_eta2(
  42.9, 1, shinella.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
shinella.by.HII.root.eta.squared <- F_to_eta2(
  1.138, 0.911, shinella.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
shinella.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, shinella.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
shinella.by.HII.effect.sizes <- tibble(
  Compartment = shinella.by.HII.compartment.eta.squared,
  Smooth_by_Root = shinella.by.HII.root.eta.squared,
  Smooth_by_Soil = shinella.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Shinella by ISC, echo = TRUE}
## Get model residuals
shinella.by.ISC.residual.df <- df.residual(
  shinella.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
shinella.by.ISC.compartment.eta.squared <- F_to_eta2(
  38.6, 1, shinella.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
shinella.by.ISC.root.eta.squared <- F_to_eta2(
  0.250, 0.708, shinella.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
shinella.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, shinella.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
shinella.by.ISC.effect.sizes <- tibble(
  Compartment = shinella.by.ISC.compartment.eta.squared,
  Smooth_by_Root = shinella.by.ISC.root.eta.squared,
  Smooth_by_Soil = shinella.by.ISC.soil.eta.squared
)
```



\newpage
### Shinella Effect Size Summary

```{r Shinella Effect Size Summary Table, echo = FALSE}
shinella.effect.sizes <- bind_rows(
  shinella.by.distance.effect.sizes,
  shinella.by.HII.effect.sizes,
  shinella.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  shinella.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Shinella abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```






\newpage
# Pathogenic Bacteria


## Legionella

### Distance

```{r Effect Size Calculations: Legionella by Distance, echo = TRUE}
## Get model residuals
legionella.by.distance.residual.df <- df.residual(
  legionella.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
legionella.by.distance.compartment.eta.squared <- F_to_eta2(
  32.59, 1, legionella.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
legionella.by.distance.root.eta.squared <- F_to_eta2(
  0.166, 0.60, legionella.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
legionella.by.distance.soil.eta.squared <- F_to_eta2(
  0.082, 0.43, legionella.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
legionella.by.distance.effect.sizes <- tibble(
  Compartment = legionella.by.distance.compartment.eta.squared,
  Smooth_by_Root = legionella.by.distance.root.eta.squared,
  Smooth_by_Soil = legionella.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Legionella by HII, echo = TRUE}
## Get model residuals
legionella.by.HII.residual.df <- df.residual(
  legionella.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
legionella.by.HII.compartment.eta.squared <- F_to_eta2(
  31.77, 1, legionella.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
legionella.by.HII.root.eta.squared <- F_to_eta2(
  0.051, 0.313, legionella.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
legionella.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.0002, legionella.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
legionella.by.HII.effect.sizes <- tibble(
  Compartment = legionella.by.HII.compartment.eta.squared,
  Smooth_by_Root = legionella.by.HII.root.eta.squared,
  Smooth_by_Soil = legionella.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Legionella by ISC, echo = TRUE}
## Get model residuals
legionella.by.ISC.residual.df <- df.residual(
  legionella.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
legionella.by.ISC.compartment.eta.squared <- F_to_eta2(
  32.89, 1, legionella.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
legionella.by.ISC.root.eta.squared <- F_to_eta2(
  0.138, 0.556, legionella.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
legionella.by.ISC.soil.eta.squared <- F_to_eta2(
  0.182, 0.631, legionella.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
legionella.by.ISC.effect.sizes <- tibble(
  Compartment = legionella.by.ISC.compartment.eta.squared,
  Smooth_by_Root = legionella.by.ISC.root.eta.squared,
  Smooth_by_Soil = legionella.by.ISC.soil.eta.squared
)
```



\newpage
### Legionella Effect Size Summary

```{r Legionella Effect Size Summary Table, echo = FALSE}
legionella.effect.sizes <- bind_rows(
  legionella.by.distance.effect.sizes,
  legionella.by.HII.effect.sizes,
  legionella.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  legionella.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Legionella abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Mycobacterium

### Distance

```{r Effect Size Calculations: Mycobacterium by Distance, echo = TRUE}
## Get model residuals
mycobacterium.by.distance.residual.df <- df.residual(
  mycobacterium.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
mycobacterium.by.distance.compartment.eta.squared <- F_to_eta2(
  100, 1, mycobacterium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
mycobacterium.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, mycobacterium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
mycobacterium.by.distance.soil.eta.squared <- F_to_eta2(
  0.122, 0.526, mycobacterium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
mycobacterium.by.distance.effect.sizes <- tibble(
  Compartment = mycobacterium.by.distance.compartment.eta.squared,
  Smooth_by_Root = mycobacterium.by.distance.root.eta.squared,
  Smooth_by_Soil = mycobacterium.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Mycobacterium by HII, echo = TRUE}
## Get model residuals
mycobacterium.by.HII.residual.df <- df.residual(
  mycobacterium.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
mycobacterium.by.HII.compartment.eta.squared <- F_to_eta2(
  99.4, 1, mycobacterium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
mycobacterium.by.HII.root.eta.squared <- F_to_eta2(
  0.058, 0.345, mycobacterium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
mycobacterium.by.HII.soil.eta.squared <- F_to_eta2(
  0.013, 0.105, mycobacterium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
mycobacterium.by.HII.effect.sizes <- tibble(
  Compartment = mycobacterium.by.HII.compartment.eta.squared,
  Smooth_by_Root = mycobacterium.by.HII.root.eta.squared,
  Smooth_by_Soil = mycobacterium.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Mycobacterium by ISC, echo = TRUE}
## Get model residuals
mycobacterium.by.ISC.residual.df <- df.residual(
  mycobacterium.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
mycobacterium.by.ISC.compartment.eta.squared <- F_to_eta2(
  98.5, 1, mycobacterium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
mycobacterium.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, mycobacterium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
mycobacterium.by.ISC.soil.eta.squared <- F_to_eta2(
  0.008, 0.067, mycobacterium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
mycobacterium.by.ISC.effect.sizes <- tibble(
  Compartment = mycobacterium.by.ISC.compartment.eta.squared,
  Smooth_by_Root = mycobacterium.by.ISC.root.eta.squared,
  Smooth_by_Soil = mycobacterium.by.ISC.soil.eta.squared
)
```



\newpage
### Mycobacterium Effect Size Summary

```{r Mycobacterium Effect Size Summary Table, echo = FALSE}
mycobacterium.effect.sizes <- bind_rows(
  mycobacterium.by.distance.effect.sizes,
  mycobacterium.by.HII.effect.sizes,
  mycobacterium.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  mycobacterium.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Mycobacterium abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Staphylococcus

### Distance

```{r Effect Size Calculations: Staphylococcus by Distance, echo = TRUE}
## Get model residuals
staphylococcus.by.distance.residual.df <- df.residual(
  staphylococcus.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
staphylococcus.by.distance.compartment.eta.squared <- F_to_eta2(
  1.836, 1, staphylococcus.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
staphylococcus.by.distance.root.eta.squared <- F_to_eta2(
  0.924, 1.91, staphylococcus.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
staphylococcus.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, staphylococcus.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
staphylococcus.by.distance.effect.sizes <- tibble(
  Compartment = staphylococcus.by.distance.compartment.eta.squared,
  Smooth_by_Root = staphylococcus.by.distance.root.eta.squared,
  Smooth_by_Soil = staphylococcus.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Staphylococcus by HII, echo = TRUE}
## Get model residuals
staphylococcus.by.HII.residual.df <- df.residual(
  staphylococcus.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
staphylococcus.by.HII.compartment.eta.squared <- F_to_eta2(
  2.717, 1, staphylococcus.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
staphylococcus.by.HII.root.eta.squared <- F_to_eta2(
  4.989, 3.523, staphylococcus.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
staphylococcus.by.HII.soil.eta.squared <- F_to_eta2(
  0.936, 2.229, staphylococcus.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
staphylococcus.by.HII.effect.sizes <- tibble(
  Compartment = staphylococcus.by.HII.compartment.eta.squared,
  Smooth_by_Root = staphylococcus.by.HII.root.eta.squared,
  Smooth_by_Soil = staphylococcus.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Staphylococcus by ISC, echo = TRUE}
## Get model residuals
staphylococcus.by.ISC.residual.df <- df.residual(
  staphylococcus.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
staphylococcus.by.ISC.compartment.eta.squared <- F_to_eta2(
  1.67, 1, staphylococcus.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
staphylococcus.by.ISC.root.eta.squared <- F_to_eta2(
  0.154, 0.586, staphylococcus.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
staphylococcus.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, staphylococcus.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
staphylococcus.by.ISC.effect.sizes <- tibble(
  Compartment = staphylococcus.by.ISC.compartment.eta.squared,
  Smooth_by_Root = staphylococcus.by.ISC.root.eta.squared,
  Smooth_by_Soil = staphylococcus.by.ISC.soil.eta.squared
)
```



\newpage
### Staphylococcus Effect Size Summary

```{r Staphylococcus Effect Size Summary Table, echo = FALSE}
staphylococcus.effect.sizes <- bind_rows(
  staphylococcus.by.distance.effect.sizes,
  staphylococcus.by.HII.effect.sizes,
  staphylococcus.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  staphylococcus.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Staphylococcus abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Stenotrophomonas

### Distance

```{r Effect Size Calculations: Stenotrophomonas by Distance, echo = TRUE}
## Get model residuals
stenotrophomonas.by.distance.residual.df <- df.residual(
  stenotrophomonas.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
stenotrophomonas.by.distance.compartment.eta.squared <- F_to_eta2(
  21.2, 1, stenotrophomonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
stenotrophomonas.by.distance.root.eta.squared <- F_to_eta2(
  0.404, 0.799, stenotrophomonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
stenotrophomonas.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, stenotrophomonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
stenotrophomonas.by.distance.effect.sizes <- tibble(
  Compartment = stenotrophomonas.by.distance.compartment.eta.squared,
  Smooth_by_Root = stenotrophomonas.by.distance.root.eta.squared,
  Smooth_by_Soil = stenotrophomonas.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Stenotrophomonas by HII, echo = TRUE}
## Get model residuals
stenotrophomonas.by.HII.residual.df <- df.residual(
  stenotrophomonas.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
stenotrophomonas.by.HII.compartment.eta.squared <- F_to_eta2(
  20.3, 1, stenotrophomonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
stenotrophomonas.by.HII.root.eta.squared <- F_to_eta2(
  0.165, 0.598, stenotrophomonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
stenotrophomonas.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, stenotrophomonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
stenotrophomonas.by.HII.effect.sizes <- tibble(
  Compartment = stenotrophomonas.by.HII.compartment.eta.squared,
  Smooth_by_Root = stenotrophomonas.by.HII.root.eta.squared,
  Smooth_by_Soil = stenotrophomonas.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Stenotrophomonas by ISC, echo = TRUE}
## Get model residuals
stenotrophomonas.by.ISC.residual.df <- df.residual(
  stenotrophomonas.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
stenotrophomonas.by.ISC.compartment.eta.squared <- F_to_eta2(
  20.8, 1, stenotrophomonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
stenotrophomonas.by.ISC.root.eta.squared <- F_to_eta2(
  0.248, 0.697, stenotrophomonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
stenotrophomonas.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, stenotrophomonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
stenotrophomonas.by.ISC.effect.sizes <- tibble(
  Compartment = stenotrophomonas.by.ISC.compartment.eta.squared,
  Smooth_by_Root = stenotrophomonas.by.ISC.root.eta.squared,
  Smooth_by_Soil = stenotrophomonas.by.ISC.soil.eta.squared
)
```



\newpage
### Stenotrophomonas Effect Size Summary

```{r Stenotrophomonas Effect Size Summary Table, echo = FALSE}
stenotrophomonas.effect.sizes <- bind_rows(
  stenotrophomonas.by.distance.effect.sizes,
  stenotrophomonas.by.HII.effect.sizes,
  stenotrophomonas.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  stenotrophomonas.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Stenotrophomonas abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Acinetobacter

### Distance

```{r Effect Size Calculations: Acinetobacter by Distance, echo = TRUE}
## Get model residuals
acinetobacter.by.distance.residual.df <- df.residual(
  acinetobacter.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
acinetobacter.by.distance.compartment.eta.squared <- F_to_eta2(
  2.542, 1, acinetobacter.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
acinetobacter.by.distance.root.eta.squared <- F_to_eta2(
  0.581, 0.864, acinetobacter.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
acinetobacter.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.001, acinetobacter.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
acinetobacter.by.distance.effect.sizes <- tibble(
  Compartment = acinetobacter.by.distance.compartment.eta.squared,
  Smooth_by_Root = acinetobacter.by.distance.root.eta.squared,
  Smooth_by_Soil = acinetobacter.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Acinetobacter by HII, echo = TRUE}
## Get model residuals
acinetobacter.by.HII.residual.df <- df.residual(
  acinetobacter.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
acinetobacter.by.HII.compartment.eta.squared <- F_to_eta2(
  2.381, 1, acinetobacter.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
acinetobacter.by.HII.root.eta.squared <- F_to_eta2(
  0.068, 0.379, acinetobacter.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
acinetobacter.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.001, acinetobacter.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
acinetobacter.by.HII.effect.sizes <- tibble(
  Compartment = acinetobacter.by.HII.compartment.eta.squared,
  Smooth_by_Root = acinetobacter.by.HII.root.eta.squared,
  Smooth_by_Soil = acinetobacter.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Acinetobacter by ISC, echo = TRUE}
## Get model residuals
acinetobacter.by.ISC.residual.df <- df.residual(
  acinetobacter.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
acinetobacter.by.ISC.compartment.eta.squared <- F_to_eta2(
  2.476, 1, acinetobacter.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
acinetobacter.by.ISC.root.eta.squared <- F_to_eta2(
  0.369, 0.779, acinetobacter.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
acinetobacter.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, acinetobacter.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
acinetobacter.by.ISC.effect.sizes <- tibble(
  Compartment = acinetobacter.by.ISC.compartment.eta.squared,
  Smooth_by_Root = acinetobacter.by.ISC.root.eta.squared,
  Smooth_by_Soil = acinetobacter.by.ISC.soil.eta.squared
)
```



\newpage
### Acinetobacter Effect Size Summary

```{r Acinetobacter Effect Size Summary Table, echo = FALSE}
acinetobacter.effect.sizes <- bind_rows(
  acinetobacter.by.distance.effect.sizes,
  acinetobacter.by.HII.effect.sizes,
  acinetobacter.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  acinetobacter.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Acinetobacter abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Clostridium

### Distance

```{r Effect Size Calculations: Clostridium by Distance, echo = TRUE}
## Get model residuals
clostridium.by.distance.residual.df <- df.residual(
  clostridium.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
clostridium.by.distance.compartment.eta.squared <- F_to_eta2(
  68.9, 1, clostridium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
clostridium.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, clostridium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
clostridium.by.distance.soil.eta.squared <- F_to_eta2(
  0.771, 0.902, clostridium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
clostridium.by.distance.effect.sizes <- tibble(
  Compartment = clostridium.by.distance.compartment.eta.squared,
  Smooth_by_Root = clostridium.by.distance.root.eta.squared,
  Smooth_by_Soil = clostridium.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Clostridium by HII, echo = TRUE}
## Get model residuals
clostridium.by.HII.residual.df <- df.residual(
  clostridium.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
clostridium.by.HII.compartment.eta.squared <- F_to_eta2(
  63.4, 1, clostridium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
clostridium.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, clostridium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
clostridium.by.HII.soil.eta.squared <- F_to_eta2(
  0.107, 0.492, clostridium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
clostridium.by.HII.effect.sizes <- tibble(
  Compartment = clostridium.by.HII.compartment.eta.squared,
  Smooth_by_Root = clostridium.by.HII.root.eta.squared,
  Smooth_by_Soil = clostridium.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Clostridium by ISC, echo = TRUE}
## Get model residuals
clostridium.by.ISC.residual.df <- df.residual(
  clostridium.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
clostridium.by.ISC.compartment.eta.squared <- F_to_eta2(
  66.9, 1, clostridium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
clostridium.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, clostridium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
clostridium.by.ISC.soil.eta.squared <- F_to_eta2(
  0.522, 0.843, clostridium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
clostridium.by.ISC.effect.sizes <- tibble(
  Compartment = clostridium.by.ISC.compartment.eta.squared,
  Smooth_by_Root = clostridium.by.ISC.root.eta.squared,
  Smooth_by_Soil = clostridium.by.ISC.soil.eta.squared
)
```



\newpage
### Clostridium Effect Size Summary

```{r Clostridium Effect Size Summary Table, echo = FALSE}
clostridium.effect.sizes <- bind_rows(
  clostridium.by.distance.effect.sizes,
  clostridium.by.HII.effect.sizes,
  clostridium.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  clostridium.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Clostridium abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Paenibacillus

### Distance

```{r Effect Size Calculations: Paenibacillus by Distance, echo = TRUE}
## Get model residuals
paenibacillus.by.distance.residual.df <- df.residual(
  paenibacillus.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
paenibacillus.by.distance.compartment.eta.squared <- F_to_eta2(
  39.8, 1, paenibacillus.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
paenibacillus.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.0001, paenibacillus.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
paenibacillus.by.distance.soil.eta.squared <- F_to_eta2(
  0.726, 0.892, paenibacillus.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
paenibacillus.by.distance.effect.sizes <- tibble(
  Compartment = paenibacillus.by.distance.compartment.eta.squared,
  Smooth_by_Root = paenibacillus.by.distance.root.eta.squared,
  Smooth_by_Soil = paenibacillus.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Paenibacillus by HII, echo = TRUE}
## Get model residuals
paenibacillus.by.HII.residual.df <- df.residual(
  paenibacillus.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
paenibacillus.by.HII.compartment.eta.squared <- F_to_eta2(
  39.2, 1, paenibacillus.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
paenibacillus.by.HII.root.eta.squared <- F_to_eta2(
  0.179, 0.617, paenibacillus.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
paenibacillus.by.HII.soil.eta.squared <- F_to_eta2(
  0.428, 0.794, paenibacillus.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
paenibacillus.by.HII.effect.sizes <- tibble(
  Compartment = paenibacillus.by.HII.compartment.eta.squared,
  Smooth_by_Root = paenibacillus.by.HII.root.eta.squared,
  Smooth_by_Soil = paenibacillus.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Paenibacillus by ISC, echo = TRUE}
## Get model residuals
paenibacillus.by.ISC.residual.df <- df.residual(
  paenibacillus.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
paenibacillus.by.ISC.compartment.eta.squared <- F_to_eta2(
  36.9, 1, paenibacillus.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
paenibacillus.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, paenibacillus.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
paenibacillus.by.ISC.soil.eta.squared <- F_to_eta2(
  0.121, 0.526, paenibacillus.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
paenibacillus.by.ISC.effect.sizes <- tibble(
  Compartment = paenibacillus.by.ISC.compartment.eta.squared,
  Smooth_by_Root = paenibacillus.by.ISC.root.eta.squared,
  Smooth_by_Soil = paenibacillus.by.ISC.soil.eta.squared
)
```



\newpage
### Paenibacillus Effect Size Summary

```{r Paenibacillus Effect Size Summary Table, echo = FALSE}
paenibacillus.effect.sizes <- bind_rows(
  paenibacillus.by.distance.effect.sizes,
  paenibacillus.by.HII.effect.sizes,
  paenibacillus.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  paenibacillus.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Paenibacillus abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```




\newpage
## Williamsia

### Distance

```{r Effect Size Calculations: Williamsia by Distance, echo = TRUE}
## Get model residuals
williamsia.by.distance.residual.df <- df.residual(
  williamsia.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
williamsia.by.distance.compartment.eta.squared <- F_to_eta2(
  0.914, 1, williamsia.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
williamsia.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, williamsia.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
williamsia.by.distance.soil.eta.squared <- F_to_eta2(
  0.312, 0.749, williamsia.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
williamsia.by.distance.effect.sizes <- tibble(
  Compartment = williamsia.by.distance.compartment.eta.squared,
  Smooth_by_Root = williamsia.by.distance.root.eta.squared,
  Smooth_by_Soil = williamsia.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Williamsia by HII, echo = TRUE}
## Get model residuals
williamsia.by.HII.residual.df <- df.residual(
  williamsia.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
williamsia.by.HII.compartment.eta.squared <- F_to_eta2(
  0.920, 1, williamsia.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
williamsia.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, williamsia.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
williamsia.by.HII.soil.eta.squared <- F_to_eta2(
  0.360, 0.764, williamsia.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
williamsia.by.HII.effect.sizes <- tibble(
  Compartment = williamsia.by.HII.compartment.eta.squared,
  Smooth_by_Root = williamsia.by.HII.root.eta.squared,
  Smooth_by_Soil = williamsia.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Williamsia by ISC, echo = TRUE}
## Get model residuals
williamsia.by.ISC.residual.df <- df.residual(
  williamsia.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
williamsia.by.ISC.compartment.eta.squared <- F_to_eta2(
  0.901, 1, williamsia.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
williamsia.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, williamsia.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
williamsia.by.ISC.soil.eta.squared <- F_to_eta2(
  0.193, 0.639, williamsia.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
williamsia.by.ISC.effect.sizes <- tibble(
  Compartment = williamsia.by.ISC.compartment.eta.squared,
  Smooth_by_Root = williamsia.by.ISC.root.eta.squared,
  Smooth_by_Soil = williamsia.by.ISC.soil.eta.squared
)
```



\newpage
### Williamsia Effect Size Summary

```{r Williamsia Effect Size Summary Table, echo = FALSE}
williamsia.effect.sizes <- bind_rows(
  williamsia.by.distance.effect.sizes,
  williamsia.by.HII.effect.sizes,
  williamsia.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  williamsia.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Williamsia abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Sphingomonas

### Distance

```{r Effect Size Calculations: Sphingomonas by Distance, echo = TRUE}
## Get model residuals
sphingomonas.by.distance.residual.df <- df.residual(
  sphingomonas.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
sphingomonas.by.distance.compartment.eta.squared <- F_to_eta2(
  76.4, 1, sphingomonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
sphingomonas.by.distance.root.eta.squared <- F_to_eta2(
  2.365, 2.433, sphingomonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
sphingomonas.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingomonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
sphingomonas.by.distance.effect.sizes <- tibble(
  Compartment = sphingomonas.by.distance.compartment.eta.squared,
  Smooth_by_Root = sphingomonas.by.distance.root.eta.squared,
  Smooth_by_Soil = sphingomonas.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Sphingomonas by HII, echo = TRUE}
## Get model residuals
sphingomonas.by.HII.residual.df <- df.residual(
  sphingomonas.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
sphingomonas.by.HII.compartment.eta.squared <- F_to_eta2(
  58.2, 1, sphingomonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
sphingomonas.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingomonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
sphingomonas.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingomonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
sphingomonas.by.HII.effect.sizes <- tibble(
  Compartment = sphingomonas.by.HII.compartment.eta.squared,
  Smooth_by_Root = sphingomonas.by.HII.root.eta.squared,
  Smooth_by_Soil = sphingomonas.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Sphingomonas by ISC, echo = TRUE}
## Get model residuals
sphingomonas.by.ISC.residual.df <- df.residual(
  sphingomonas.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
sphingomonas.by.ISC.compartment.eta.squared <- F_to_eta2(
  58.2, 1, sphingomonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
sphingomonas.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingomonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
sphingomonas.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingomonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
sphingomonas.by.ISC.effect.sizes <- tibble(
  Compartment = sphingomonas.by.ISC.compartment.eta.squared,
  Smooth_by_Root = sphingomonas.by.ISC.root.eta.squared,
  Smooth_by_Soil = sphingomonas.by.ISC.soil.eta.squared
)
```



\newpage
### Sphingomonas Effect Size Summary

```{r Sphingomonas Effect Size Summary Table, echo = FALSE}
sphingomonas.effect.sizes <- bind_rows(
  sphingomonas.by.distance.effect.sizes,
  sphingomonas.by.HII.effect.sizes,
  sphingomonas.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  sphingomonas.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Sphingomonas abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Xanthomonas

### Distance

```{r Effect Size Calculations: Xanthomonas by Distance, echo = TRUE}
## Get model residuals
xanthomonas.by.distance.residual.df <- df.residual(
  xanthomonas.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
xanthomonas.by.distance.compartment.eta.squared <- F_to_eta2(
  18.2, 1, xanthomonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
xanthomonas.by.distance.root.eta.squared <- F_to_eta2(
  0.656, 0.886, xanthomonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
xanthomonas.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, xanthomonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
xanthomonas.by.distance.effect.sizes <- tibble(
  Compartment = xanthomonas.by.distance.compartment.eta.squared,
  Smooth_by_Root = xanthomonas.by.distance.root.eta.squared,
  Smooth_by_Soil = xanthomonas.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Xanthomonas by HII, echo = TRUE}
## Get model residuals
xanthomonas.by.HII.residual.df <- df.residual(
  xanthomonas.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
xanthomonas.by.HII.compartment.eta.squared <- F_to_eta2(
  19.6, 1, xanthomonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
xanthomonas.by.HII.root.eta.squared <- F_to_eta2(
  1.302, 0.922, xanthomonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
xanthomonas.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, xanthomonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
xanthomonas.by.HII.effect.sizes <- tibble(
  Compartment = xanthomonas.by.HII.compartment.eta.squared,
  Smooth_by_Root = xanthomonas.by.HII.root.eta.squared,
  Smooth_by_Soil = xanthomonas.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Xanthomonas by ISC, echo = TRUE}
## Get model residuals
xanthomonas.by.ISC.residual.df <- df.residual(
  xanthomonas.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
xanthomonas.by.ISC.compartment.eta.squared <- F_to_eta2(
  17.8, 1, xanthomonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
xanthomonas.by.ISC.root.eta.squared <- F_to_eta2(
  0.480, 0.834, xanthomonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
xanthomonas.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, xanthomonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
xanthomonas.by.ISC.effect.sizes <- tibble(
  Compartment = xanthomonas.by.ISC.compartment.eta.squared,
  Smooth_by_Root = xanthomonas.by.ISC.root.eta.squared,
  Smooth_by_Soil = xanthomonas.by.ISC.soil.eta.squared
)
```



\newpage
### Xanthomonas Effect Size Summary

```{r Xanthomonas Effect Size Summary Table, echo = FALSE}
xanthomonas.effect.sizes <- bind_rows(
  xanthomonas.by.distance.effect.sizes,
  xanthomonas.by.HII.effect.sizes,
  xanthomonas.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  xanthomonas.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Xanthomonas abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Rhizobacter

### Distance

```{r Effect Size Calculations: Rhizobacter by Distance, echo = TRUE}
## Get model residuals
rhizobacter.by.distance.residual.df <- df.residual(
  rhizobacter.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
rhizobacter.by.distance.compartment.eta.squared <- F_to_eta2(
  115.9, 1, rhizobacter.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
rhizobacter.by.distance.root.eta.squared <- F_to_eta2(
  1.684, 3.462, rhizobacter.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
rhizobacter.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, rhizobacter.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
rhizobacter.by.distance.effect.sizes <- tibble(
  Compartment = rhizobacter.by.distance.compartment.eta.squared,
  Smooth_by_Root = rhizobacter.by.distance.root.eta.squared,
  Smooth_by_Soil = rhizobacter.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Rhizobacter by HII, echo = TRUE}
## Get model residuals
rhizobacter.by.HII.residual.df <- df.residual(
  rhizobacter.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
rhizobacter.by.HII.compartment.eta.squared <- F_to_eta2(
  97.8, 1, rhizobacter.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
rhizobacter.by.HII.root.eta.squared <- F_to_eta2(
  0.245, 0.688, rhizobacter.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
rhizobacter.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, rhizobacter.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
rhizobacter.by.HII.effect.sizes <- tibble(
  Compartment = rhizobacter.by.HII.compartment.eta.squared,
  Smooth_by_Root = rhizobacter.by.HII.root.eta.squared,
  Smooth_by_Soil = rhizobacter.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Rhizobacter by ISC, echo = TRUE}
## Get model residuals
rhizobacter.by.ISC.residual.df <- df.residual(
  rhizobacter.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
rhizobacter.by.ISC.compartment.eta.squared <- F_to_eta2(
  97.4, 1, rhizobacter.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
rhizobacter.by.ISC.root.eta.squared <- F_to_eta2(
  0.210, 0.660, rhizobacter.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
rhizobacter.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, rhizobacter.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
rhizobacter.by.ISC.effect.sizes <- tibble(
  Compartment = rhizobacter.by.ISC.compartment.eta.squared,
  Smooth_by_Root = rhizobacter.by.ISC.root.eta.squared,
  Smooth_by_Soil = rhizobacter.by.ISC.soil.eta.squared
)
```



\newpage
### Rhizobacter Effect Size Summary

```{r Rhizobacter Effect Size Summary Table, echo = FALSE}
rhizobacter.effect.sizes <- bind_rows(
  rhizobacter.by.distance.effect.sizes,
  rhizobacter.by.HII.effect.sizes,
  rhizobacter.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  rhizobacter.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Rhizobacter abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```




\newpage
## Agrobacterium

### Distance

```{r Effect Size Calculations: Agrobacterium by Distance, echo = TRUE}
## Get model residuals
agrobacterium.by.distance.residual.df <- df.residual(
  agrobacterium.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
agrobacterium.by.distance.compartment.eta.squared <- F_to_eta2(
  59.8, 1, agrobacterium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
agrobacterium.by.distance.root.eta.squared <- F_to_eta2(
  2.438, 2.650, agrobacterium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
agrobacterium.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, agrobacterium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
agrobacterium.by.distance.effect.sizes <- tibble(
  Compartment = agrobacterium.by.distance.compartment.eta.squared,
  Smooth_by_Root = agrobacterium.by.distance.root.eta.squared,
  Smooth_by_Soil = agrobacterium.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Agrobacterium by HII, echo = TRUE}
## Get model residuals
agrobacterium.by.HII.residual.df <- df.residual(
  agrobacterium.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
agrobacterium.by.HII.compartment.eta.squared <- F_to_eta2(
  89.6, 1, agrobacterium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
agrobacterium.by.HII.root.eta.squared <- F_to_eta2(
  7.399, 4.810, agrobacterium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
agrobacterium.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, agrobacterium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
agrobacterium.by.HII.effect.sizes <- tibble(
  Compartment = agrobacterium.by.HII.compartment.eta.squared,
  Smooth_by_Root = agrobacterium.by.HII.root.eta.squared,
  Smooth_by_Soil = agrobacterium.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Agrobacterium by ISC, echo = TRUE}
## Get model residuals
agrobacterium.by.ISC.residual.df <- df.residual(
  agrobacterium.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
agrobacterium.by.ISC.compartment.eta.squared <- F_to_eta2(
  52.4, 1, agrobacterium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
agrobacterium.by.ISC.root.eta.squared <- F_to_eta2(
  1.189, 2.325, agrobacterium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
agrobacterium.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, agrobacterium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
agrobacterium.by.ISC.effect.sizes <- tibble(
  Compartment = agrobacterium.by.ISC.compartment.eta.squared,
  Smooth_by_Root = agrobacterium.by.ISC.root.eta.squared,
  Smooth_by_Soil = agrobacterium.by.ISC.soil.eta.squared
)
```



\newpage
### Agrobacterium Effect Size Summary

```{r Agrobacterium Effect Size Summary Table, echo = FALSE}
agrobacterium.effect.sizes <- bind_rows(
  agrobacterium.by.distance.effect.sizes,
  agrobacterium.by.HII.effect.sizes,
  agrobacterium.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  agrobacterium.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Agrobacterium abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```









\newpage
# Ecosystem Function Bacteria

\newpage
## Nitrosomonas

### Distance

```{r Effect Size Calculations: Nitrosomonas by Distance, echo = TRUE}
## Get model residuals
nitrosomonas.by.distance.residual.df <- df.residual(
  nitrosomonas.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
nitrosomonas.by.distance.compartment.eta.squared <- F_to_eta2(
  109.3, 1, nitrosomonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
nitrosomonas.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, nitrosomonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
nitrosomonas.by.distance.soil.eta.squared <- F_to_eta2(
  7.068, 2.644, nitrosomonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
nitrosomonas.by.distance.effect.sizes <- tibble(
  Compartment = nitrosomonas.by.distance.compartment.eta.squared,
  Smooth_by_Root = nitrosomonas.by.distance.root.eta.squared,
  Smooth_by_Soil = nitrosomonas.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Nitrosomonas by HII, echo = TRUE}
## Get model residuals
nitrosomonas.by.HII.residual.df <- df.residual(
  nitrosomonas.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
nitrosomonas.by.HII.compartment.eta.squared <- F_to_eta2(
  15.3, 1, nitrosomonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
nitrosomonas.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, nitrosomonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
nitrosomonas.by.HII.soil.eta.squared <- F_to_eta2(
  0.952, 0.896, nitrosomonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
nitrosomonas.by.HII.effect.sizes <- tibble(
  Compartment = nitrosomonas.by.HII.compartment.eta.squared,
  Smooth_by_Root = nitrosomonas.by.HII.root.eta.squared,
  Smooth_by_Soil = nitrosomonas.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Nitrosomonas by ISC, echo = TRUE}
## Get model residuals
nitrosomonas.by.ISC.residual.df <- df.residual(
  nitrosomonas.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
nitrosomonas.by.ISC.compartment.eta.squared <- F_to_eta2(
  8.9, 1, nitrosomonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
nitrosomonas.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, nitrosomonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
nitrosomonas.by.ISC.soil.eta.squared <- F_to_eta2(
  1.236, 0.960, nitrosomonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
nitrosomonas.by.ISC.effect.sizes <- tibble(
  Compartment = nitrosomonas.by.ISC.compartment.eta.squared,
  Smooth_by_Root = nitrosomonas.by.ISC.root.eta.squared,
  Smooth_by_Soil = nitrosomonas.by.ISC.soil.eta.squared
)
```



\newpage
### Nitrosomonas Effect Size Summary

```{r Nitrosomonas Effect Size Summary Table, echo = FALSE}
nitrosomonas.effect.sizes <- bind_rows(
  nitrosomonas.by.distance.effect.sizes,
  nitrosomonas.by.HII.effect.sizes,
  nitrosomonas.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  nitrosomonas.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Nitrosomonas abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Nitrospira

### Distance

```{r Effect Size Calculations: Nitrospira by Distance, echo = TRUE}
## Get model residuals
nitrospira.by.distance.residual.df <- df.residual(
  nitrospira.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
nitrospira.by.distance.compartment.eta.squared <- F_to_eta2(
  354.2, 1, nitrospira.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
nitrospira.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, nitrospira.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
nitrospira.by.distance.soil.eta.squared <- F_to_eta2(
  9.207, 2.403, nitrospira.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
nitrospira.by.distance.effect.sizes <- tibble(
  Compartment = nitrospira.by.distance.compartment.eta.squared,
  Smooth_by_Root = nitrospira.by.distance.root.eta.squared,
  Smooth_by_Soil = nitrospira.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Nitrospira by HII, echo = TRUE}
## Get model residuals
nitrospira.by.HII.residual.df <- df.residual(
  nitrospira.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
nitrospira.by.HII.compartment.eta.squared <- F_to_eta2(
  250.7, 1, nitrospira.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
nitrospira.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, nitrospira.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
nitrospira.by.HII.soil.eta.squared <- F_to_eta2(
  4.6160, 3.051, nitrospira.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
nitrospira.by.HII.effect.sizes <- tibble(
  Compartment = nitrospira.by.HII.compartment.eta.squared,
  Smooth_by_Root = nitrospira.by.HII.root.eta.squared,
  Smooth_by_Soil = nitrospira.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Nitrospira by ISC, echo = TRUE}
## Get model residuals
nitrospira.by.ISC.residual.df <- df.residual(
  nitrospira.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
nitrospira.by.ISC.compartment.eta.squared <- F_to_eta2(
  201.7, 1, nitrospira.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
nitrospira.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, nitrospira.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
nitrospira.by.ISC.soil.eta.squared <- F_to_eta2(
  2.240, 1.018, nitrospira.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
nitrospira.by.ISC.effect.sizes <- tibble(
  Compartment = nitrospira.by.ISC.compartment.eta.squared,
  Smooth_by_Root = nitrospira.by.ISC.root.eta.squared,
  Smooth_by_Soil = nitrospira.by.ISC.soil.eta.squared
)
```



\newpage
### Nitrospira Effect Size Summary

```{r Nitrospira Effect Size Summary Table, echo = FALSE}
nitrospira.effect.sizes <- bind_rows(
  nitrospira.by.distance.effect.sizes,
  nitrospira.by.HII.effect.sizes,
  nitrospira.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  nitrospira.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Nitrospira abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Desulfuromonas

### Distance

```{r Effect Size Calculations: Desulfuromonas by Distance, echo = TRUE}
## Get model residuals
desulfuromonas.by.distance.residual.df <- df.residual(
  desulfuromonas.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
desulfuromonas.by.distance.compartment.eta.squared <- F_to_eta2(
  38.8, 1, desulfuromonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
desulfuromonas.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, desulfuromonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
desulfuromonas.by.distance.soil.eta.squared <- F_to_eta2(
  2.346, 1.041, desulfuromonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
desulfuromonas.by.distance.effect.sizes <- tibble(
  Compartment = desulfuromonas.by.distance.compartment.eta.squared,
  Smooth_by_Root = desulfuromonas.by.distance.root.eta.squared,
  Smooth_by_Soil = desulfuromonas.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Desulfuromonas by HII, echo = TRUE}
## Get model residuals
desulfuromonas.by.HII.residual.df <- df.residual(
  desulfuromonas.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
desulfuromonas.by.HII.compartment.eta.squared <- F_to_eta2(
  34.6, 1, desulfuromonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
desulfuromonas.by.HII.root.eta.squared <- F_to_eta2(
  0.0001, 0.00001, desulfuromonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
desulfuromonas.by.HII.soil.eta.squared <- F_to_eta2(
  1.277, 0.920, desulfuromonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
desulfuromonas.by.HII.effect.sizes <- tibble(
  Compartment = desulfuromonas.by.HII.compartment.eta.squared,
  Smooth_by_Root = desulfuromonas.by.HII.root.eta.squared,
  Smooth_by_Soil = desulfuromonas.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Desulfuromonas by ISC, echo = TRUE}
## Get model residuals
desulfuromonas.by.ISC.residual.df <- df.residual(
  desulfuromonas.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
desulfuromonas.by.ISC.compartment.eta.squared <- F_to_eta2(
  36.3, 1, desulfuromonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
desulfuromonas.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, desulfuromonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
desulfuromonas.by.ISC.soil.eta.squared <- F_to_eta2(
  1.715, 1.003, desulfuromonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
desulfuromonas.by.ISC.effect.sizes <- tibble(
  Compartment = desulfuromonas.by.ISC.compartment.eta.squared,
  Smooth_by_Root = desulfuromonas.by.ISC.root.eta.squared,
  Smooth_by_Soil = desulfuromonas.by.ISC.soil.eta.squared
)
```



\newpage
### Desulfuromonas Effect Size Summary

```{r Desulfuromonas Effect Size Summary Table, echo = FALSE}
desulfuromonas.effect.sizes <- bind_rows(
  desulfuromonas.by.distance.effect.sizes,
  desulfuromonas.by.HII.effect.sizes,
  desulfuromonas.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  desulfuromonas.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Desulfuromonas abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```




\newpage
## Aciditerrimonas

### Distance

```{r Effect Size Calculations: Aciditerrimonas by Distance, echo = TRUE}
## Get model residuals
aciditerrimonas.by.distance.residual.df <- df.residual(
  aciditerrimonas.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
aciditerrimonas.by.distance.compartment.eta.squared <- F_to_eta2(
  42.2, 1, aciditerrimonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
aciditerrimonas.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, aciditerrimonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
aciditerrimonas.by.distance.soil.eta.squared <- F_to_eta2(
  4.109, 1.148, aciditerrimonas.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
aciditerrimonas.by.distance.effect.sizes <- tibble(
  Compartment = aciditerrimonas.by.distance.compartment.eta.squared,
  Smooth_by_Root = aciditerrimonas.by.distance.root.eta.squared,
  Smooth_by_Soil = aciditerrimonas.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Aciditerrimonas by HII, echo = TRUE}
## Get model residuals
aciditerrimonas.by.HII.residual.df <- df.residual(
  aciditerrimonas.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
aciditerrimonas.by.HII.compartment.eta.squared <- F_to_eta2(
  32.6, 1, aciditerrimonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
aciditerrimonas.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, aciditerrimonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
aciditerrimonas.by.HII.soil.eta.squared <- F_to_eta2(
  1.450, 0.929, aciditerrimonas.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
aciditerrimonas.by.HII.effect.sizes <- tibble(
  Compartment = aciditerrimonas.by.HII.compartment.eta.squared,
  Smooth_by_Root = aciditerrimonas.by.HII.root.eta.squared,
  Smooth_by_Soil = aciditerrimonas.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Aciditerrimonas by ISC, echo = TRUE}
## Get model residuals
aciditerrimonas.by.ISC.residual.df <- df.residual(
  aciditerrimonas.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
aciditerrimonas.by.ISC.compartment.eta.squared <- F_to_eta2(
  30.8, 1, aciditerrimonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
aciditerrimonas.by.ISC.root.eta.squared <- F_to_eta2(
  0.0001, 0.00001, aciditerrimonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
aciditerrimonas.by.ISC.soil.eta.squared <- F_to_eta2(
  0.950, 0.931, aciditerrimonas.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
aciditerrimonas.by.ISC.effect.sizes <- tibble(
  Compartment = aciditerrimonas.by.ISC.compartment.eta.squared,
  Smooth_by_Root = aciditerrimonas.by.ISC.root.eta.squared,
  Smooth_by_Soil = aciditerrimonas.by.ISC.soil.eta.squared
)
```



\newpage
### Aciditerrimonas Effect Size Summary

```{r Aciditerrimonas Effect Size Summary Table, echo = FALSE}
aciditerrimonas.effect.sizes <- bind_rows(
  aciditerrimonas.by.distance.effect.sizes,
  aciditerrimonas.by.HII.effect.sizes,
  aciditerrimonas.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  aciditerrimonas.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Aciditerrimonas abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```




\newpage
## Nitrosospira

### Distance

```{r Effect Size Calculations: Nitrosospira by Distance, echo = TRUE}
## Get model residuals
nitrosospira.by.distance.residual.df <- df.residual(
  nitrosospira.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
nitrosospira.by.distance.compartment.eta.squared <- F_to_eta2(
  237.1, 1, nitrosospira.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
nitrosospira.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, nitrosospira.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
nitrosospira.by.distance.soil.eta.squared <- F_to_eta2(
  3.362, 3.494, nitrosospira.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
nitrosospira.by.distance.effect.sizes <- tibble(
  Compartment = nitrosospira.by.distance.compartment.eta.squared,
  Smooth_by_Root = nitrosospira.by.distance.root.eta.squared,
  Smooth_by_Soil = nitrosospira.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Nitrosospira by HII, echo = TRUE}
## Get model residuals
nitrosospira.by.HII.residual.df <- df.residual(
  nitrosospira.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
nitrosospira.by.HII.compartment.eta.squared <- F_to_eta2(
  171.3, 1, nitrosospira.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
nitrosospira.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, nitrosospira.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
nitrosospira.by.HII.soil.eta.squared <- F_to_eta2(
  0.334, 0.751, nitrosospira.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
nitrosospira.by.HII.effect.sizes <- tibble(
  Compartment = nitrosospira.by.HII.compartment.eta.squared,
  Smooth_by_Root = nitrosospira.by.HII.root.eta.squared,
  Smooth_by_Soil = nitrosospira.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Nitrosospira by ISC, echo = TRUE}
## Get model residuals
nitrosospira.by.ISC.residual.df <- df.residual(
  nitrosospira.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
nitrosospira.by.ISC.compartment.eta.squared <- F_to_eta2(
  201.7, 1, nitrosospira.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
nitrosospira.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, nitrosospira.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
nitrosospira.by.ISC.soil.eta.squared <- F_to_eta2(
  1.730, 1.002, nitrosospira.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
nitrosospira.by.ISC.effect.sizes <- tibble(
  Compartment = nitrosospira.by.ISC.compartment.eta.squared,
  Smooth_by_Root = nitrosospira.by.ISC.root.eta.squared,
  Smooth_by_Soil = nitrosospira.by.ISC.soil.eta.squared
)
```



\newpage
### Nitrosospira Effect Size Summary

```{r Nitrosospira Effect Size Summary Table, echo = FALSE}
nitrosospira.effect.sizes <- bind_rows(
  nitrosospira.by.distance.effect.sizes,
  nitrosospira.by.HII.effect.sizes,
  nitrosospira.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  nitrosospira.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Nitrosospira abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Sphingopyxis

### Distance

```{r Effect Size Calculations: Sphingopyxis by Distance, echo = TRUE}
## Get model residuals
sphingopyxis.by.distance.residual.df <- df.residual(
  sphingopyxis.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
sphingopyxis.by.distance.compartment.eta.squared <- F_to_eta2(
  84.7, 1, sphingopyxis.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
sphingopyxis.by.distance.root.eta.squared <- F_to_eta2(
  0.087, 0.444, sphingopyxis.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
sphingopyxis.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingopyxis.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
sphingopyxis.by.distance.effect.sizes <- tibble(
  Compartment = sphingopyxis.by.distance.compartment.eta.squared,
  Smooth_by_Root = sphingopyxis.by.distance.root.eta.squared,
  Smooth_by_Soil = sphingopyxis.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Sphingopyxis by HII, echo = TRUE}
## Get model residuals
sphingopyxis.by.HII.residual.df <- df.residual(
  sphingopyxis.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
sphingopyxis.by.HII.compartment.eta.squared <- F_to_eta2(
  83.8, 1, sphingopyxis.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
sphingopyxis.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingopyxis.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
sphingopyxis.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingopyxis.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
sphingopyxis.by.HII.effect.sizes <- tibble(
  Compartment = sphingopyxis.by.HII.compartment.eta.squared,
  Smooth_by_Root = sphingopyxis.by.HII.root.eta.squared,
  Smooth_by_Soil = sphingopyxis.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Sphingopyxis by ISC, echo = TRUE}
## Get model residuals
sphingopyxis.by.ISC.residual.df <- df.residual(
  sphingopyxis.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
sphingopyxis.by.ISC.compartment.eta.squared <- F_to_eta2(
  87.2, 1, sphingopyxis.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
sphingopyxis.by.ISC.root.eta.squared <- F_to_eta2(
  0.311, 0.750, sphingopyxis.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
sphingopyxis.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingopyxis.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
sphingopyxis.by.ISC.effect.sizes <- tibble(
  Compartment = sphingopyxis.by.ISC.compartment.eta.squared,
  Smooth_by_Root = sphingopyxis.by.ISC.root.eta.squared,
  Smooth_by_Soil = sphingopyxis.by.ISC.soil.eta.squared
)
```



\newpage
### Sphingopyxis Effect Size Summary

```{r Sphingopyxis Effect Size Summary Table, echo = FALSE}
sphingopyxis.effect.sizes <- bind_rows(
  sphingopyxis.by.distance.effect.sizes,
  sphingopyxis.by.HII.effect.sizes,
  sphingopyxis.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  sphingopyxis.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Sphingopyxis abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```






\newpage
## Cytophaga

### Distance

```{r Effect Size Calculations: Cytophaga by Distance, echo = TRUE}
## Get model residuals
cytophaga.by.distance.residual.df <- df.residual(
  cytophaga.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
cytophaga.by.distance.compartment.eta.squared <- F_to_eta2(
  34.1, 1, cytophaga.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
cytophaga.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, cytophaga.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
cytophaga.by.distance.soil.eta.squared <- F_to_eta2(
  5.849, 6.008, cytophaga.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
cytophaga.by.distance.effect.sizes <- tibble(
  Compartment = cytophaga.by.distance.compartment.eta.squared,
  Smooth_by_Root = cytophaga.by.distance.root.eta.squared,
  Smooth_by_Soil = cytophaga.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Cytophaga by HII, echo = TRUE}
## Get model residuals
cytophaga.by.HII.residual.df <- df.residual(
  cytophaga.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
cytophaga.by.HII.compartment.eta.squared <- F_to_eta2(
  25.5, 1, cytophaga.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
cytophaga.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, cytophaga.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
cytophaga.by.HII.soil.eta.squared <- F_to_eta2(
  2.483, 0.958, cytophaga.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
cytophaga.by.HII.effect.sizes <- tibble(
  Compartment = cytophaga.by.HII.compartment.eta.squared,
  Smooth_by_Root = cytophaga.by.HII.root.eta.squared,
  Smooth_by_Soil = cytophaga.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Cytophaga by ISC, echo = TRUE}
## Get model residuals
cytophaga.by.ISC.residual.df <- df.residual(
  cytophaga.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
cytophaga.by.ISC.compartment.eta.squared <- F_to_eta2(
  29.8, 1, cytophaga.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
cytophaga.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, cytophaga.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
cytophaga.by.ISC.soil.eta.squared <- F_to_eta2(
  4.148, 2.495, cytophaga.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
cytophaga.by.ISC.effect.sizes <- tibble(
  Compartment = cytophaga.by.ISC.compartment.eta.squared,
  Smooth_by_Root = cytophaga.by.ISC.root.eta.squared,
  Smooth_by_Soil = cytophaga.by.ISC.soil.eta.squared
)
```



\newpage
### Cytophaga Effect Size Summary

```{r Cytophaga Effect Size Summary Table, echo = FALSE}
cytophaga.effect.sizes <- bind_rows(
  cytophaga.by.distance.effect.sizes,
  cytophaga.by.HII.effect.sizes,
  cytophaga.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  cytophaga.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Cytophaga abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Paracoccus

### Distance

```{r Effect Size Calculations: Paracoccus by Distance, echo = TRUE}
## Get model residuals
paracoccus.by.distance.residual.df <- df.residual(
  paracoccus.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
paracoccus.by.distance.compartment.eta.squared <- F_to_eta2(
  6.6, 1, paracoccus.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
paracoccus.by.distance.root.eta.squared <- F_to_eta2(
  1.064, 0.958, paracoccus.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
paracoccus.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.001, paracoccus.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
paracoccus.by.distance.effect.sizes <- tibble(
  Compartment = paracoccus.by.distance.compartment.eta.squared,
  Smooth_by_Root = paracoccus.by.distance.root.eta.squared,
  Smooth_by_Soil = paracoccus.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Paracoccus by HII, echo = TRUE}
## Get model residuals
paracoccus.by.HII.residual.df <- df.residual(
  paracoccus.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
paracoccus.by.HII.compartment.eta.squared <- F_to_eta2(
  6.2, 1, paracoccus.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
paracoccus.by.HII.root.eta.squared <- F_to_eta2(
  0.552, 0.832, paracoccus.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
paracoccus.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.001, paracoccus.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
paracoccus.by.HII.effect.sizes <- tibble(
  Compartment = paracoccus.by.HII.compartment.eta.squared,
  Smooth_by_Root = paracoccus.by.HII.root.eta.squared,
  Smooth_by_Soil = paracoccus.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Paracoccus by ISC, echo = TRUE}
## Get model residuals
paracoccus.by.ISC.residual.df <- df.residual(
  paracoccus.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
paracoccus.by.ISC.compartment.eta.squared <- F_to_eta2(
  7.2, 1, paracoccus.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
paracoccus.by.ISC.root.eta.squared <- F_to_eta2(
  1.783, 1.021, paracoccus.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
paracoccus.by.ISC.soil.eta.squared <- F_to_eta2(
  0.020, 0.152, paracoccus.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
paracoccus.by.ISC.effect.sizes <- tibble(
  Compartment = paracoccus.by.ISC.compartment.eta.squared,
  Smooth_by_Root = paracoccus.by.ISC.root.eta.squared,
  Smooth_by_Soil = paracoccus.by.ISC.soil.eta.squared
)
```



\newpage
### Paracoccus Effect Size Summary

```{r Paracoccus Effect Size Summary Table, echo = FALSE}
paracoccus.effect.sizes <- bind_rows(
  paracoccus.by.distance.effect.sizes,
  paracoccus.by.HII.effect.sizes,
  paracoccus.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  paracoccus.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Paracoccus abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Novosphingobium

### Distance

```{r Effect Size Calculations: Novosphingobium by Distance, echo = TRUE}
## Get model residuals
novosphingobium.by.distance.residual.df <- df.residual(
  novosphingobium.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
novosphingobium.by.distance.compartment.eta.squared <- F_to_eta2(
  296.5, 1, novosphingobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
novosphingobium.by.distance.root.eta.squared <- F_to_eta2(
  0.279, 0.737, novosphingobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
novosphingobium.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, novosphingobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
novosphingobium.by.distance.effect.sizes <- tibble(
  Compartment = novosphingobium.by.distance.compartment.eta.squared,
  Smooth_by_Root = novosphingobium.by.distance.root.eta.squared,
  Smooth_by_Soil = novosphingobium.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Novosphingobium by HII, echo = TRUE}
## Get model residuals
novosphingobium.by.HII.residual.df <- df.residual(
  novosphingobium.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
novosphingobium.by.HII.compartment.eta.squared <- F_to_eta2(
  285.9, 1, novosphingobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
novosphingobium.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, novosphingobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
novosphingobium.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, novosphingobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
novosphingobium.by.HII.effect.sizes <- tibble(
  Compartment = novosphingobium.by.HII.compartment.eta.squared,
  Smooth_by_Root = novosphingobium.by.HII.root.eta.squared,
  Smooth_by_Soil = novosphingobium.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Novosphingobium by ISC, echo = TRUE}
## Get model residuals
novosphingobium.by.ISC.residual.df <- df.residual(
  novosphingobium.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
novosphingobium.by.ISC.compartment.eta.squared <- F_to_eta2(
  287.3, 1, novosphingobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
novosphingobium.by.ISC.root.eta.squared <- F_to_eta2(
  0.036, 0.246, novosphingobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
novosphingobium.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, novosphingobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
novosphingobium.by.ISC.effect.sizes <- tibble(
  Compartment = novosphingobium.by.ISC.compartment.eta.squared,
  Smooth_by_Root = novosphingobium.by.ISC.root.eta.squared,
  Smooth_by_Soil = novosphingobium.by.ISC.soil.eta.squared
)
```



\newpage
### Novosphingobium Effect Size Summary

```{r Novosphingobium Effect Size Summary Table, echo = FALSE}
novosphingobium.effect.sizes <- bind_rows(
  novosphingobium.by.distance.effect.sizes,
  novosphingobium.by.HII.effect.sizes,
  novosphingobium.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  novosphingobium.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Novosphingobium abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Devosia

### Distance

```{r Effect Size Calculations: Devosia by Distance, echo = TRUE}
## Get model residuals
devosia.by.distance.residual.df <- df.residual(
  devosia.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
devosia.by.distance.compartment.eta.squared <- F_to_eta2(
  388.3, 1, devosia.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
devosia.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, devosia.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
devosia.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, devosia.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
devosia.by.distance.effect.sizes <- tibble(
  Compartment = devosia.by.distance.compartment.eta.squared,
  Smooth_by_Root = devosia.by.distance.root.eta.squared,
  Smooth_by_Soil = devosia.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Devosia by HII, echo = TRUE}
## Get model residuals
devosia.by.HII.residual.df <- df.residual(
  devosia.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
devosia.by.HII.compartment.eta.squared <- F_to_eta2(
  391.5, 1, devosia.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
devosia.by.HII.root.eta.squared <- F_to_eta2(
  0.063, 0.361, devosia.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
devosia.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, devosia.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
devosia.by.HII.effect.sizes <- tibble(
  Compartment = devosia.by.HII.compartment.eta.squared,
  Smooth_by_Root = devosia.by.HII.root.eta.squared,
  Smooth_by_Soil = devosia.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Devosia by ISC, echo = TRUE}
## Get model residuals
devosia.by.ISC.residual.df <- df.residual(
  devosia.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
devosia.by.ISC.compartment.eta.squared <- F_to_eta2(
  388.3, 1, devosia.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
devosia.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, devosia.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
devosia.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, devosia.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
devosia.by.ISC.effect.sizes <- tibble(
  Compartment = devosia.by.ISC.compartment.eta.squared,
  Smooth_by_Root = devosia.by.ISC.root.eta.squared,
  Smooth_by_Soil = devosia.by.ISC.soil.eta.squared
)
```



\newpage
### Devosia Effect Size Summary

```{r Devosia Effect Size Summary Table, echo = FALSE}
devosia.effect.sizes <- bind_rows(
  devosia.by.distance.effect.sizes,
  devosia.by.HII.effect.sizes,
  devosia.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  devosia.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Devosia abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```






\newpage
## Streptomyces

### Distance

```{r Effect Size Calculations: Streptomyces by Distance, echo = TRUE}
## Get model residuals
streptomyces.by.distance.residual.df <- df.residual(
  streptomyces.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
streptomyces.by.distance.compartment.eta.squared <- F_to_eta2(
  78.2, 1, streptomyces.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
streptomyces.by.distance.root.eta.squared <- F_to_eta2(
  0.192, 0.646, streptomyces.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
streptomyces.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, streptomyces.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
streptomyces.by.distance.effect.sizes <- tibble(
  Compartment = streptomyces.by.distance.compartment.eta.squared,
  Smooth_by_Root = streptomyces.by.distance.root.eta.squared,
  Smooth_by_Soil = streptomyces.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Streptomyces by HII, echo = TRUE}
## Get model residuals
streptomyces.by.HII.residual.df <- df.residual(
  streptomyces.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
streptomyces.by.HII.compartment.eta.squared <- F_to_eta2(
  76.2, 1, streptomyces.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
streptomyces.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, streptomyces.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
streptomyces.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, streptomyces.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
streptomyces.by.HII.effect.sizes <- tibble(
  Compartment = streptomyces.by.HII.compartment.eta.squared,
  Smooth_by_Root = streptomyces.by.HII.root.eta.squared,
  Smooth_by_Soil = streptomyces.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Streptomyces by ISC, echo = TRUE}
## Get model residuals
streptomyces.by.ISC.residual.df <- df.residual(
  streptomyces.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
streptomyces.by.ISC.compartment.eta.squared <- F_to_eta2(
  76.2, 1, streptomyces.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
streptomyces.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, streptomyces.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
streptomyces.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, streptomyces.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
streptomyces.by.ISC.effect.sizes <- tibble(
  Compartment = streptomyces.by.ISC.compartment.eta.squared,
  Smooth_by_Root = streptomyces.by.ISC.root.eta.squared,
  Smooth_by_Soil = streptomyces.by.ISC.soil.eta.squared
)
```



\newpage
### Streptomyces Effect Size Summary

```{r Streptomyces Effect Size Summary Table, echo = FALSE}
streptomyces.effect.sizes <- bind_rows(
  streptomyces.by.distance.effect.sizes,
  streptomyces.by.HII.effect.sizes,
  streptomyces.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  streptomyces.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Streptomyces abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Sphingobium

### Distance

```{r Effect Size Calculations: Sphingobium by Distance, echo = TRUE}
## Get model residuals
sphingobium.by.distance.residual.df <- df.residual(
  sphingobium.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
sphingobium.by.distance.compartment.eta.squared <- F_to_eta2(
  74.6, 1, sphingobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
sphingobium.by.distance.root.eta.squared <- F_to_eta2(
  0.122, 0.528, sphingobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
sphingobium.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingobium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
sphingobium.by.distance.effect.sizes <- tibble(
  Compartment = sphingobium.by.distance.compartment.eta.squared,
  Smooth_by_Root = sphingobium.by.distance.root.eta.squared,
  Smooth_by_Soil = sphingobium.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Sphingobium by HII, echo = TRUE}
## Get model residuals
sphingobium.by.HII.residual.df <- df.residual(
  sphingobium.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
sphingobium.by.HII.compartment.eta.squared <- F_to_eta2(
  75.1, 1, sphingobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
sphingobium.by.HII.root.eta.squared <- F_to_eta2(
  0.176, 0.613, sphingobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
sphingobium.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingobium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
sphingobium.by.HII.effect.sizes <- tibble(
  Compartment = sphingobium.by.HII.compartment.eta.squared,
  Smooth_by_Root = sphingobium.by.HII.root.eta.squared,
  Smooth_by_Soil = sphingobium.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Sphingobium by ISC, echo = TRUE}
## Get model residuals
sphingobium.by.ISC.residual.df <- df.residual(
  sphingobium.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
sphingobium.by.ISC.compartment.eta.squared <- F_to_eta2(
  73.4, 1, sphingobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
sphingobium.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
sphingobium.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, sphingobium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
sphingobium.by.ISC.effect.sizes <- tibble(
  Compartment = sphingobium.by.ISC.compartment.eta.squared,
  Smooth_by_Root = sphingobium.by.ISC.root.eta.squared,
  Smooth_by_Soil = sphingobium.by.ISC.soil.eta.squared
)
```



\newpage
### Sphingobium Effect Size Summary

```{r Sphingobium Effect Size Summary Table, echo = FALSE}
sphingobium.effect.sizes <- bind_rows(
  sphingobium.by.distance.effect.sizes,
  sphingobium.by.HII.effect.sizes,
  sphingobium.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  sphingobium.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Sphingobium abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```






\newpage
## Desulfosporosinus

### Distance

```{r Effect Size Calculations: Desulfosporosinus by Distance, echo = TRUE}
## Get model residuals
desulfosporosinus.by.distance.residual.df <- df.residual(
  desulfosporosinus.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
desulfosporosinus.by.distance.compartment.eta.squared <- F_to_eta2(
  50.0, 1, desulfosporosinus.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
desulfosporosinus.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.001, desulfosporosinus.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
desulfosporosinus.by.distance.soil.eta.squared <- F_to_eta2(
  0.632, 1.641, desulfosporosinus.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
desulfosporosinus.by.distance.effect.sizes <- tibble(
  Compartment = desulfosporosinus.by.distance.compartment.eta.squared,
  Smooth_by_Root = desulfosporosinus.by.distance.root.eta.squared,
  Smooth_by_Soil = desulfosporosinus.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Desulfosporosinus by HII, echo = TRUE}
## Get model residuals
desulfosporosinus.by.HII.residual.df <- df.residual(
  desulfosporosinus.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
desulfosporosinus.by.HII.compartment.eta.squared <- F_to_eta2(
  53.4, 1, desulfosporosinus.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
desulfosporosinus.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, desulfosporosinus.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
desulfosporosinus.by.HII.soil.eta.squared <- F_to_eta2(
  1.176, 2.957, desulfosporosinus.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
desulfosporosinus.by.HII.effect.sizes <- tibble(
  Compartment = desulfosporosinus.by.HII.compartment.eta.squared,
  Smooth_by_Root = desulfosporosinus.by.HII.root.eta.squared,
  Smooth_by_Soil = desulfosporosinus.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Desulfosporosinus by ISC, echo = TRUE}
## Get model residuals
desulfosporosinus.by.ISC.residual.df <- df.residual(
  desulfosporosinus.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
desulfosporosinus.by.ISC.compartment.eta.squared <- F_to_eta2(
  65.2, 1, desulfosporosinus.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
desulfosporosinus.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, desulfosporosinus.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
desulfosporosinus.by.ISC.soil.eta.squared <- F_to_eta2(
  3.111, 5.460, desulfosporosinus.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
desulfosporosinus.by.ISC.effect.sizes <- tibble(
  Compartment = desulfosporosinus.by.ISC.compartment.eta.squared,
  Smooth_by_Root = desulfosporosinus.by.ISC.root.eta.squared,
  Smooth_by_Soil = desulfosporosinus.by.ISC.soil.eta.squared
)
```



\newpage
### Desulfosporosinus Effect Size Summary

```{r Desulfosporosinus Effect Size Summary Table, echo = FALSE}
desulfosporosinus.effect.sizes <- bind_rows(
  desulfosporosinus.by.distance.effect.sizes,
  desulfosporosinus.by.HII.effect.sizes,
  desulfosporosinus.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  desulfosporosinus.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Desulfosporosinus abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```






\newpage
## Desulfocapsa

### Distance

```{r Effect Size Calculations: Desulfocapsa by Distance, echo = TRUE}
## Get model residuals
desulfocapsa.by.distance.residual.df <- df.residual(
  desulfocapsa.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
desulfocapsa.by.distance.compartment.eta.squared <- F_to_eta2(
  14.2, 1, desulfocapsa.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
desulfocapsa.by.distance.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, desulfocapsa.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
desulfocapsa.by.distance.soil.eta.squared <- F_to_eta2(
  0.816, 0.920, desulfocapsa.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
desulfocapsa.by.distance.effect.sizes <- tibble(
  Compartment = desulfocapsa.by.distance.compartment.eta.squared,
  Smooth_by_Root = desulfocapsa.by.distance.root.eta.squared,
  Smooth_by_Soil = desulfocapsa.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Desulfocapsa by HII, echo = TRUE}
## Get model residuals
desulfocapsa.by.HII.residual.df <- df.residual(
  desulfocapsa.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
desulfocapsa.by.HII.compartment.eta.squared <- F_to_eta2(
  14.2, 1, desulfocapsa.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
desulfocapsa.by.HII.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, desulfocapsa.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
desulfocapsa.by.HII.soil.eta.squared <- F_to_eta2(
  0.823, 0.881, desulfocapsa.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
desulfocapsa.by.HII.effect.sizes <- tibble(
  Compartment = desulfocapsa.by.HII.compartment.eta.squared,
  Smooth_by_Root = desulfocapsa.by.HII.root.eta.squared,
  Smooth_by_Soil = desulfocapsa.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Desulfocapsa by ISC, echo = TRUE}
## Get model residuals
desulfocapsa.by.ISC.residual.df <- df.residual(
  desulfocapsa.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
desulfocapsa.by.ISC.compartment.eta.squared <- F_to_eta2(
  14.1, 1, desulfocapsa.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
desulfocapsa.by.ISC.root.eta.squared <- F_to_eta2(
  0.00001, 0.00001, desulfocapsa.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
desulfocapsa.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, desulfocapsa.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
desulfocapsa.by.ISC.effect.sizes <- tibble(
  Compartment = desulfocapsa.by.ISC.compartment.eta.squared,
  Smooth_by_Root = desulfocapsa.by.ISC.root.eta.squared,
  Smooth_by_Soil = desulfocapsa.by.ISC.soil.eta.squared
)
```



\newpage
### Desulfocapsa Effect Size Summary

```{r Desulfocapsa Effect Size Summary Table, echo = FALSE}
desulfocapsa.effect.sizes <- bind_rows(
  desulfocapsa.by.distance.effect.sizes,
  desulfocapsa.by.HII.effect.sizes,
  desulfocapsa.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  desulfocapsa.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Desulfocapsa abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Phyllobacterium

### Distance

```{r Effect Size Calculations: Phyllobacterium by Distance, echo = TRUE}
## Get model residuals
phyllobacterium.by.distance.residual.df <- df.residual(
  phyllobacterium.by.distance.GAM
)

## Calculate effect sizes
# Compartment (parametric)
phyllobacterium.by.distance.compartment.eta.squared <- F_to_eta2(
  38.9, 1, phyllobacterium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by root
phyllobacterium.by.distance.root.eta.squared <- F_to_eta2(
  0.056, 0.339, phyllobacterium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of distance by soil
phyllobacterium.by.distance.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, phyllobacterium.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
phyllobacterium.by.distance.effect.sizes <- tibble(
  Compartment = phyllobacterium.by.distance.compartment.eta.squared,
  Smooth_by_Root = phyllobacterium.by.distance.root.eta.squared,
  Smooth_by_Soil = phyllobacterium.by.distance.soil.eta.squared
)
```



\newpage
### Human Influence Index

```{r Effect Size Calculations: Phyllobacterium by HII, echo = TRUE}
## Get model residuals
phyllobacterium.by.HII.residual.df <- df.residual(
  phyllobacterium.by.HII.GAM
)

## Calculate effect sizes
# Compartment (parametric)
phyllobacterium.by.HII.compartment.eta.squared <- F_to_eta2(
  41.6, 1, phyllobacterium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by root
phyllobacterium.by.HII.root.eta.squared <- F_to_eta2(
  0.574, 0.838, phyllobacterium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of HII by soil
phyllobacterium.by.HII.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, phyllobacterium.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
phyllobacterium.by.HII.effect.sizes <- tibble(
  Compartment = phyllobacterium.by.HII.compartment.eta.squared,
  Smooth_by_Root = phyllobacterium.by.HII.root.eta.squared,
  Smooth_by_Soil = phyllobacterium.by.HII.soil.eta.squared
)
```



\newpage
### Mean ISC

```{r Effect Size Calculations: Phyllobacterium by ISC, echo = TRUE}
## Get model residuals
phyllobacterium.by.ISC.residual.df <- df.residual(
  phyllobacterium.by.ISC.GAM
)

## Calculate effect sizes
# Compartment (parametric)
phyllobacterium.by.ISC.compartment.eta.squared <- F_to_eta2(
  41.2, 1, phyllobacterium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by root
phyllobacterium.by.ISC.root.eta.squared <- F_to_eta2(
  0.487, 0.834, phyllobacterium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# Smooth of ISC by soil
phyllobacterium.by.ISC.soil.eta.squared <- F_to_eta2(
  0.00001, 0.00001, phyllobacterium.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
phyllobacterium.by.ISC.effect.sizes <- tibble(
  Compartment = phyllobacterium.by.ISC.compartment.eta.squared,
  Smooth_by_Root = phyllobacterium.by.ISC.root.eta.squared,
  Smooth_by_Soil = phyllobacterium.by.ISC.soil.eta.squared
)
```



\newpage
### Phyllobacterium Effect Size Summary

```{r Phyllobacterium Effect Size Summary Table, echo = FALSE}
phyllobacterium.effect.sizes <- bind_rows(
  phyllobacterium.by.distance.effect.sizes,
  phyllobacterium.by.HII.effect.sizes,
  phyllobacterium.by.ISC.effect.sizes
) %>%
  add_column(Urbanization_Metric = c("Distance", "HII", "ISC")) %>%
  as_tibble() %>%
  select(Urbanization_Metric, Compartment:Smooth_by_Soil)

kable(
  phyllobacterium.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the Phyllobacterium abundance GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
# Carbon & Nitrogen Effect Sizes

## Soil Total Carbon

```{r Effect Size Calculations: Soil Total Carbon, echo = TRUE}
## Get model residuals
# Distance
soil.total.C.by.distance.residual.df <- df.residual(
  soil.total.C.by.distance.GAM
)
# HII
soil.total.C.by.HII.residual.df <- df.residual(
  soil.total.C.by.HII.GAM
)
# ISC
soil.total.C.by.ISC.residual.df <- df.residual(
  soil.total.C.by.ISC.GAM
)

## Calculate effect sizes
# Distance
soil.total.C.by.distance.eta.squared <- F_to_eta2(
  1.604, 2.518, soil.total.C.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# HII
soil.total.C.by.HII.eta.squared <- F_to_eta2(
  0.679, 0.859, soil.total.C.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# ISC
soil.total.C.by.ISC.eta.squared <- F_to_eta2(
  1.867, 2.452, soil.total.C.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
soil.total.C.effect.sizes <- tibble(
  Distance = soil.total.C.by.distance.eta.squared,
  HII = soil.total.C.by.HII.eta.squared,
  ISC = soil.total.C.by.ISC.eta.squared
)
```

\vspace{10pt}

```{r Soil Total Carbon Effect Size Summary Table, echo = FALSE}
kable(
  soil.total.C.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the soil total C GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Soil Delta 13C

```{r Effect Size Calculations: Soil Delta 13C, echo = TRUE}
## Get model residuals
# Distance
soil.delta.13C.by.distance.residual.df <- df.residual(
  soil.delta.13C.by.distance.GAM
)
# HII
soil.delta.13C.by.HII.residual.df <- df.residual(
  soil.delta.13C.by.HII.GAM
)
# ISC
soil.delta.13C.by.ISC.residual.df <- df.residual(
  soil.delta.13C.by.ISC.GAM
)

## Calculate effect sizes
# Distance
soil.delta.13C.by.distance.eta.squared <- F_to_eta2(
  2.141, 1.039, soil.delta.13C.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# HII
soil.delta.13C.by.HII.eta.squared <- F_to_eta2(
  1.039, 0.904, soil.delta.13C.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# ISC
soil.delta.13C.by.ISC.eta.squared <- F_to_eta2(
  0.954, 0.939, soil.delta.13C.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
soil.delta.13C.effect.sizes <- tibble(
  Distance = soil.delta.13C.by.distance.eta.squared,
  HII = soil.delta.13C.by.HII.eta.squared,
  ISC = soil.delta.13C.by.ISC.eta.squared
)
```

\vspace{10pt}

```{r Soil Delta 13C Effect Size Summary Table, echo = FALSE}
kable(
  soil.delta.13C.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the soil delta 13C GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```




\newpage
## Leaf Total Carbon

```{r Effect Size Calculations: Leaf Total Carbon, echo = TRUE}
## Get model residuals
# Distance
leaf.total.C.by.distance.residual.df <- df.residual(
  leaf.total.C.by.distance.GAM
)
# HII
leaf.total.C.by.HII.residual.df <- df.residual(
  leaf.total.C.by.HII.GAM
)
# ISC
leaf.total.C.by.ISC.residual.df <- df.residual(
  leaf.total.C.by.ISC.GAM
)

## Calculate effect sizes
# Distance
leaf.total.C.by.distance.eta.squared <- F_to_eta2(
  0.00001, 0.00001, leaf.total.C.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# HII
leaf.total.C.by.HII.eta.squared <- F_to_eta2(
  0.00001, 0.00001, leaf.total.C.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# ISC
leaf.total.C.by.ISC.eta.squared <- F_to_eta2(
  0.872, 1.841, leaf.total.C.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
leaf.total.C.effect.sizes <- tibble(
  Distance = leaf.total.C.by.distance.eta.squared,
  HII = leaf.total.C.by.HII.eta.squared,
  ISC = leaf.total.C.by.ISC.eta.squared
)
```

\vspace{10pt}

```{r Leaf Total Carbon Effect Size Summary Table, echo = FALSE}
kable(
  leaf.total.C.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the leaf total C GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Leaf Delta 13C

```{r Effect Size Calculations: Leaf Delta 13C, echo = TRUE}
## Get model residuals
# Distance
leaf.delta.13C.by.distance.residual.df <- df.residual(
  leaf.delta.13C.by.distance.GAM
)
# HII
leaf.delta.13C.by.HII.residual.df <- df.residual(
  leaf.delta.13C.by.HII.GAM
)
# ISC
leaf.delta.13C.by.ISC.residual.df <- df.residual(
  leaf.delta.13C.by.ISC.GAM
)

## Calculate effect sizes
# Distance
leaf.delta.13C.by.distance.eta.squared <- F_to_eta2(
  0.279, 0.730, leaf.delta.13C.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# HII
leaf.delta.13C.by.HII.eta.squared <- F_to_eta2(
  0.043, 0.278, leaf.delta.13C.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# ISC
leaf.delta.13C.by.ISC.eta.squared <- F_to_eta2(
  0.087, 0.442, leaf.delta.13C.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
leaf.delta.13C.effect.sizes <- tibble(
  Distance = leaf.delta.13C.by.distance.eta.squared,
  HII = leaf.delta.13C.by.HII.eta.squared,
  ISC = leaf.delta.13C.by.ISC.eta.squared
)
```

\vspace{10pt}

```{r Leaf Delta 13C Effect Size Summary Table, echo = FALSE}
kable(
  leaf.delta.13C.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the leaf delta 13C GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Soil Total Nitrogen

```{r Effect Size Calculations: Soil Total Nitrogen, echo = TRUE}
## Get model residuals
# Distance
soil.total.N.by.distance.residual.df <- df.residual(
  soil.total.N.by.distance.GAM
)
# HII
soil.total.N.by.HII.residual.df <- df.residual(
  soil.total.N.by.HII.GAM
)
# ISC
soil.total.N.by.ISC.residual.df <- df.residual(
  soil.total.N.by.ISC.GAM
)

## Calculate effect sizes
# Distance
soil.total.N.by.distance.eta.squared <- F_to_eta2(
  0.546, 0.851, soil.total.N.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# HII
soil.total.N.by.HII.eta.squared <- F_to_eta2(
  0.024, 0.179, soil.total.N.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# ISC
soil.total.N.by.ISC.eta.squared <- F_to_eta2(
  0.141, 0.563, soil.total.N.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
soil.total.N.effect.sizes <- tibble(
  Distance = soil.total.N.by.distance.eta.squared,
  HII = soil.total.N.by.HII.eta.squared,
  ISC = soil.total.N.by.ISC.eta.squared
)
```

\vspace{10pt}

```{r Soil Total Nitrogen Effect Size Summary Table, echo = FALSE}
kable(
  soil.total.N.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the soil total N GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Soil Delta 15N

```{r Effect Size Calculations: Soil Delta 15N, echo = TRUE}
## Get model residuals
# Distance
soil.delta.15N.by.distance.residual.df <- df.residual(
  soil.delta.15N.by.distance.GAM
)
# HII
soil.delta.15N.by.HII.residual.df <- df.residual(
  soil.delta.15N.by.HII.GAM
)
# ISC
soil.delta.15N.by.ISC.residual.df <- df.residual(
  soil.delta.15N.by.ISC.GAM
)

## Calculate effect sizes
# Distance
soil.delta.15N.by.distance.eta.squared <- F_to_eta2(
  1.306, 0.968, soil.delta.15N.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# HII
soil.delta.15N.by.HII.eta.squared <- F_to_eta2(
  1.521, 0.932, soil.delta.15N.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# ISC
soil.delta.15N.by.ISC.eta.squared <- F_to_eta2(
  1.192, 0.950, soil.delta.15N.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
soil.delta.15N.effect.sizes <- tibble(
  Distance = soil.delta.15N.by.distance.eta.squared,
  HII = soil.delta.15N.by.HII.eta.squared,
  ISC = soil.delta.15N.by.ISC.eta.squared
)
```

\vspace{10pt}

```{r Soil Delta 15N Effect Size Summary Table, echo = FALSE}
kable(
  soil.delta.15N.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the soil delta 15N GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```




\newpage
## Leaf Total Nitrogen

```{r Effect Size Calculations: Leaf Total Nitrogen, echo = TRUE}
## Get model residuals
# Distance
leaf.total.N.by.distance.residual.df <- df.residual(
  leaf.total.N.by.distance.GAM
)
# HII
leaf.total.N.by.HII.residual.df <- df.residual(
  leaf.total.N.by.HII.GAM
)
# ISC
leaf.total.N.by.ISC.residual.df <- df.residual(
  leaf.total.N.by.ISC.GAM
)

## Calculate effect sizes
# Distance
leaf.total.N.by.distance.eta.squared <- F_to_eta2(
  3.065, 3.070, leaf.total.N.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# HII
leaf.total.N.by.HII.eta.squared <- F_to_eta2(
  0.029, 0.207, leaf.total.N.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# ISC
leaf.total.N.by.ISC.eta.squared <- F_to_eta2(
  1.364, 1.916, leaf.total.N.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
leaf.total.N.effect.sizes <- tibble(
  Distance = leaf.total.N.by.distance.eta.squared,
  HII = leaf.total.N.by.HII.eta.squared,
  ISC = leaf.total.N.by.ISC.eta.squared
)
```

\vspace{10pt}

```{r Leaf Total Nitrogen Effect Size Summary Table, echo = FALSE}
kable(
  leaf.total.N.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the leaf total N GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```





\newpage
## Leaf Delta 15N

```{r Effect Size Calculations: Leaf Delta 15N, echo = TRUE}
## Get model residuals
# Distance
leaf.delta.15N.by.distance.residual.df <- df.residual(
  leaf.delta.15N.by.distance.GAM
)
# HII
leaf.delta.15N.by.HII.residual.df <- df.residual(
  leaf.delta.15N.by.HII.GAM
)
# ISC
leaf.delta.15N.by.ISC.residual.df <- df.residual(
  leaf.delta.15N.by.ISC.GAM
)

## Calculate effect sizes
# Distance
leaf.delta.15N.by.distance.eta.squared <- F_to_eta2(
  0.090, 0.450, leaf.delta.15N.by.distance.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# HII
leaf.delta.15N.by.HII.eta.squared <- F_to_eta2(
  0.028, 0.200, leaf.delta.15N.by.HII.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()
# ISC
leaf.delta.15N.by.ISC.eta.squared <- F_to_eta2(
  0.127, 0.537, leaf.delta.15N.by.ISC.residual.df
) %>%
  select(Eta2_partial) %>%
  as.numeric()

## Set tibble of effect sizes
leaf.delta.15N.effect.sizes <- tibble(
  Distance = leaf.delta.15N.by.distance.eta.squared,
  HII = leaf.delta.15N.by.HII.eta.squared,
  ISC = leaf.delta.15N.by.ISC.eta.squared
)
```

\vspace{10pt}

```{r Leaf Delta 15N Effect Size Summary Table, echo = FALSE}
kable(
  leaf.delta.15N.effect.sizes,
  booktabs = TRUE,
  digits = 5,
  caption = "Summary of effect sizes (partial eta-squared) for the leaf delta 15N GAMs."
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```









\newpage
# R Session Information

```{r R Packages, echo = FALSE}
df_session_packages <- devtools::session_info()$packages %>%
  as.data.frame(.) %>%
  filter(attached == TRUE) %>%
  dplyr::select(loadedversion, date) %>%
  rownames_to_column()

colnames(df_session_packages) <- c("Package", "Loaded Version", "Date")

kable(
  df_session_packages,
  booktabs = TRUE,
  caption = "Packages required for data management and analysis."
) %>%
  kable_styling(
    full_width = FALSE,
    latex_options = c("HOLD_position", "striped")
  )
```
